### 2024-10-12 paper/paper.qmd
Uploading starter files

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Sameeck Bhatia
  - Sean Chua
thanks: "Code and data are available at: [https://github.com/SameeckBhatia/2024-US-Elections](https://github.com/SameeckBhatia/2024-US-Elections)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-10-13 scripts/00-simulate_data.R
Simulating mock data

@@ -1,52 +1,33 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of Australian electoral divisions, including the 
-  #state and party that won each division.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Simulates a mock dataset of surveyed individuals
+# Author: Sameeck Bhatia
+# Date: 12 October 2024
+# Contact: sameeck.bhatia@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: The `tidyverse` package must be installed
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Any other information needed? None
 
 
 #### Workspace setup ####
 library(tidyverse)
-set.seed(853)
+set.seed(12)
 
 
 #### Simulate data ####
-# State names
-states <- c(
-  "New South Wales",
-  "Victoria",
-  "Queensland",
-  "South Australia",
-  "Western Australia",
-  "Tasmania",
-  "Northern Territory",
-  "Australian Capital Territory"
-)
+states <- c("AL", "AK", "AR", "AZ", "CA", "CO", "CT")
+races <- c("w", "b", "h", "a", "n", "o")
+parties <- c("d", "r", "i")
+voter_types <- c("registered", "likely")
 
-# Political parties
-parties <- c("Labor", "Liberal", "Greens", "National", "Other")
-
-# Create a dataset by randomly assigning states and parties to divisions
-analysis_data <- tibble(
-  division = paste("Division", 1:151),  # Add "Division" to make it a character
-  state = sample(
-    states,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.25, 0.25, 0.15, 0.1, 0.1, 0.1, 0.025, 0.025) # Rough state population distribution
-  ),
-  party = sample(
-    parties,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.40, 0.40, 0.05, 0.1, 0.05) # Rough party distribution
-  )
+simulated_data <- data.frame(
+  "id" = sample(10000:99999, 10000, replace = FALSE),
+  "state" = sample(states, 10000, replace = TRUE),
+  "race" = sample(races, 10000, replace = TRUE, prob = c(60, 13, 19, 6, 1, 1)),
+  "party" = sample(parties, 10000, replace = TRUE, prob = c(51, 47, 2)),
[…]

### 2024-10-13 scripts/00-simulate_data.R
Simulating mock data

@@ -11,42 +11,24 @@
 
 #### Workspace setup ####
 library(tidyverse)
-set.seed(853)
+set.seed(12)
 
 
 #### Simulate data ####
-# State names
-states <- c(
-  "New South Wales",
-  "Victoria",
-  "Queensland",
-  "South Australia",
-  "Western Australia",
-  "Tasmania",
-  "Northern Territory",
-  "Australian Capital Territory"
-)
+states <- c("AL", "AK", "AR", "AZ", "CA", "CO", "CT")
+races <- c("w", "b", "h", "a", "n", "o")
+parties <- c("d", "r", "i")
+voter_types <- c("registered", "likely")
 
-# Political parties
-parties <- c("Labor", "Liberal", "Greens", "National", "Other")
-
-# Create a dataset by randomly assigning states and parties to divisions
-analysis_data <- tibble(
-  division = paste("Division", 1:151),  # Add "Division" to make it a character
-  state = sample(
-    states,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.25, 0.25, 0.15, 0.1, 0.1, 0.1, 0.025, 0.025) # Rough state population distribution
-  ),
-  party = sample(
-    parties,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.40, 0.40, 0.05, 0.1, 0.05) # Rough party distribution
-  )
+simulated_data <- data.frame(
+  "id" = sample(10000:99999, 10000, replace = FALSE),
+  "state" = sample(states, 10000, replace = TRUE),
+  "race" = sample(races, 10000, replace = TRUE, prob = c(60, 13, 19, 6, 1, 1)),
+  "party" = sample(parties, 10000, replace = TRUE, prob = c(51, 47, 2)),
+  "last_election" = sample(parties, 10000, replace = TRUE, prob = c(48, 46, 6)),
+  "voter_type" = sample(voter_types, 10000, replace = TRUE, prob = c(66, 34))
 )
 
 
 #### Save data ####
-write_csv(analysis_data, "data/00-simulated_data/simulated_data.csv")
+write_csv(simulated_data, "data/00-simulated_data/simulated_data.csv")

### 2024-10-13 paper/paper.qmd
Updating the paper

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Race to the Ballot Box: Will Demographics Decide a Winner This Year?"
+subtitle: "A Regressional Approach to Race and Political Preferences in the 2024 US Elections and Insights on the Next"
 author: 
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Proin semper lobortis ante quis euismod.
+Praesent iaculis, nunc sed sagittis dignissim, metus eros venenatis nunc, in posuere risus felis eget nisi.
+Praesent pulvinar metus velit, sit amet tincidunt dolor consectetur id.
+Praesent mi nisi, venenatis nec euismod a, vehicula et nisl.
+In hac habitasse platea dictumst.
+Sed tristique ligula id suscipit convallis.
+Donec eget orci in felis consequat fringilla id sit amet lacus."
 format: pdf
@@
 
-Overview paragraph
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Curabitur tincidunt nec eros ut consequat.
+Donec consectetur purus non nisl posuere, et gravida erat bibendum.
+Donec tincidunt tortor suscipit dignissim convallis.
+Pellentesque elit libero, varius a orci tincidunt, rhoncus sodales augue.
+Donec egestas, risus vitae feugiat efficitur, nunc velit euismod tellus, at dictum neque orci id nisi.
+Ut sit amet nisl suscipit, elementum nisl quis, volutpat sem.
+Phasellus mauris sapien, facilisis at eros eu, consequat gravida lorem.
+Praesent pulvinar blandit enim sed aliquam.
+Cras purus nunc, auctor ut lectus sit amet, facilisis dignissim ligula.
+Cras ligula odio, eleifend sit amet sem ut, sollicitudin imperdiet massa.
+Vivamus eget mi bibendum, vehicula ipsum a, pretium felis.
+Maecenas semper vel nisi fringilla luctus.
 
-Estimand paragraph
+Donec eleifend tortor eu diam convallis, eu dictum nunc tincidunt.
+Nunc consectetur sapien arcu, id gravida arcu pulvinar id.
+Nam dignissim nisl ac ornare maximus.
+Nullam eget vulputate libero.
+Vestibulum vitae sapien risus.
+Vivamus facilisis orci semper, tincidunt massa at, faucibus sem.
+Ut ac augue elementum, bibendum justo ornare, porta tortor.
+Vestibulum vitae turpis orci.
+Sed ultrices ante metus, vel efficitur eros feugiat luctus.
+Nulla at tincidunt nunc, et dapibus nisi.
+Proin feugiat, elit pellentesque lobortis pellentesque, magna odio efficitur diam, eget finibus arcu tortor sit amet diam.
+Duis malesuada lacus sit amet dui auctor pellentesque.
+Sed fermentum lectus id vulputate euismod.
+Duis ultrices magna eu leo consequat consectetur.
+Nulla facilisi.
 
-Results paragraph
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Curabitur tincidunt nec eros ut consequat.
+Donec consectetur purus non nisl posuere, et gravida erat bibendum.
+Donec tincidunt tortor suscipit dignissim convallis.
+Pellentesque elit libero, varius a orci tincidunt, rhoncus sodales augue.
+Donec egestas, risus vitae feugiat efficitur, nunc velit euismod tellus, at dictum neque orci id nisi.
+Ut sit amet nisl suscipit, elementum nisl quis, volutpat sem.
+Phasellus mauris sapien, facilisis at eros eu, consequat gravida lorem.
+Praesent pulvinar blandit enim sed aliquam.
+Cras purus nunc, auctor ut lectus sit amet, facilisis dignissim ligula.
+Cras ligula odio, eleifend sit amet sem ut, sollicitudin imperdiet massa.
+Vivamus eget mi bibendum, vehicula ipsum a, pretium felis.
+Maecenas semper vel nisi fringilla luctus.
 
-Why it matters paragraph
-
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+Donec eleifend tortor eu diam convallis, eu dictum nunc tincidunt.
+Nunc consectetur sapien arcu, id gravida arcu pulvinar id.
+Nam dignissim nisl ac ornare maximus.
+Nullam eget vulputate libero.
+Vestibulum vitae sapien risus.
+Vivamus facilisis orci semper, tincidunt massa at, faucibus sem.
+Ut ac augue elementum, bibendum justo ornare, porta tortor.
+Vestibulum vitae turpis orci.
+Sed ultrices ante metus, vel efficitur eros feugiat luctus.
+Nulla at tincidunt nunc, et dapibus nisi.
+Proin feugiat, elit pellentesque lobortis pellentesque, magna odio efficitur diam, eget finibus arcu tortor sit amet diam.
+Duis malesuada lacus sit amet dui auctor pellentesque.
+Sed fermentum lectus id vulputate euismod.
+Duis ultrices magna eu leo consequat consectetur.
+Nulla facilisi.
 
@@
 
-Overview text
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
+Mauris non libero vel ligula tincidunt consequat.
+Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
+Vivamus feugiat et quam ut consequat.
+Aenean mollis ullamcorper facilisis.
+Vivamus scelerisque lectus et elementum vulputate.
+Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
+Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
+Curabitur vitae tortor nec ligula scelerisque rutrum.
+Nullam feugiat odio metus.
+Cras id convallis ante, ut ornare velit.
+Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
 
@@
 
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
+Mauris non libero vel ligula tincidunt consequat.
+Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
+Vivamus feugiat et quam ut consequat.
+Aenean mollis ullamcorper facilisis.
+Vivamus scelerisque lectus et elementum vulputate.
+Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
+Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
+Curabitur vitae tortor nec ligula scelerisque rutrum.
+Nullam feugiat odio metus.
+Cras id convallis ante, ut ornare velit.
+Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
 
@@
 
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
-
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
-
-```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
-
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
-```
-
-Talk way more about it.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
+Mauris non libero vel ligula tincidunt consequat.
+Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
+Vivamus feugiat et quam ut consequat.
+Aenean mollis ullamcorper facilisis.
+Vivamus scelerisque lectus et elementum vulputate.
+Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
+Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
+Curabitur vitae tortor nec ligula scelerisque rutrum.
+Nullam feugiat odio metus.
+Cras id convallis ante, ut ornare velit.
+Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
 
@@
 
-Add graphs, tables and text.
-
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
+Mauris non libero vel ligula tincidunt consequat.
+Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
+Vivamus feugiat et quam ut consequat.
+Aenean mollis ullamcorper facilisis.
+Vivamus scelerisque lectus et elementum vulputate.
+Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
+Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
+Curabitur vitae tortor nec ligula scelerisque rutrum.
+Nullam feugiat odio metus.
+Cras id convallis ante, ut ornare velit.
+Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
 
@@
 
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
+Mauris non libero vel ligula tincidunt consequat.
+Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
+Vivamus feugiat et quam ut consequat.
+Aenean mollis ullamcorper facilisis.
+Vivamus scelerisque lectus et elementum vulputate.
+Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
+Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
+Curabitur vitae tortor nec ligula scelerisque rutrum.
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
-
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-### Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
+Mauris non libero vel ligula tincidunt consequat.
+Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
+Vivamus feugiat et quam ut consequat.
+Aenean mollis ullamcorper facilisis.
+Vivamus scelerisque lectus et elementum vulputate.
+Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
+Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
+Curabitur vitae tortor nec ligula scelerisque rutrum.
+Nullam feugiat odio metus.
+Cras id convallis ante, ut ornare velit.
+Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
 
@@
 
-Our results are summarized in @tbl-modelresults.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
+Mauris non libero vel ligula tincidunt consequat.
+Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
+Vivamus feugiat et quam ut consequat.
+Aenean mollis ullamcorper facilisis.
+Vivamus scelerisque lectus et elementum vulputate.
+Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
+Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
+Curabitur vitae tortor nec ligula scelerisque rutrum.
+Nullam feugiat odio metus.
+Cras id convallis ante, ut ornare velit.
+Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
 
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
-```
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
+Mauris non libero vel ligula tincidunt consequat.
+Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
+Vivamus feugiat et quam ut consequat.
+Aenean mollis ullamcorper facilisis.
+Vivamus scelerisque lectus et elementum vulputate.
+Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
+Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
+Curabitur vitae tortor nec ligula scelerisque rutrum.
+Nullam feugiat odio metus.
+Cras id convallis ante, ut ornare velit.
+Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
 
@@
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
+Mauris non libero vel ligula tincidunt consequat.
+Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
+Vivamus feugiat et quam ut consequat.
+Aenean mollis ullamcorper facilisis.
+Vivamus scelerisque lectus et elementum vulputate.
+Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
+Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
+Curabitur vitae tortor nec ligula scelerisque rutrum.
+Nullam feugiat odio metus.
+Cras id convallis ante, ut ornare velit.
+Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
 
@@
 
-Please don't use these as sub-heading labels - change them to be what your point actually is.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
+Mauris non libero vel ligula tincidunt consequat.
+Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
+Vivamus feugiat et quam ut consequat.
+Aenean mollis ullamcorper facilisis.
+Vivamus scelerisque lectus et elementum vulputate.
+Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
+Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
+Curabitur vitae tortor nec ligula scelerisque rutrum.
+Nullam feugiat odio metus.
+Cras id convallis ante, ut ornare velit.
+Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
 
@@
 
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
+Mauris non libero vel ligula tincidunt consequat.
+Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
+Vivamus feugiat et quam ut consequat.
+Aenean mollis ullamcorper facilisis.
+Vivamus scelerisque lectus et elementum vulputate.
+Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
+Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
+Curabitur vitae tortor nec ligula scelerisque rutrum.
+Nullam feugiat odio metus.
+Cras id convallis ante, ut ornare velit.
+Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
+
 ## Weaknesses and next steps
 
-Weaknesses and next steps should also be included.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
+Mauris non libero vel ligula tincidunt consequat.
+Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
+Vivamus feugiat et quam ut consequat.
+Aenean mollis ullamcorper facilisis.
+Vivamus scelerisque lectus et elementum vulputate.
+Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
+Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
+Curabitur vitae tortor nec ligula scelerisque rutrum.
+Nullam feugiat odio metus.
+Cras id convallis ante, ut ornare velit.
+Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
 
@@
 
-# Appendix {-}
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
-
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
-```
+# Appendix {.unnumbered}
 

### 2024-10-14 scripts/00-simulate_data.R
Updating the simulated data

@@ -1,10 +1,11 @@
 #### Preamble ####
-# Purpose: Simulates a mock dataset of surveyed individuals
+# Purpose: Simulates a mock dataset of surveyed individuals.
 # Author: Sameeck Bhatia
-# Date: 12 October 2024
+# Date: 14 October 2024
 # Contact: sameeck.bhatia@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: The `tidyverse` package must be installed
+# Pre-requisites: 
+#   - The `tidyverse` package must be installed and loaded
 # Any other information needed? None
 
 
@@ -14,20 +15,25 @@ set.seed(12)
 
 
 #### Simulate data ####
-states <- c("AL", "AK", "AR", "AZ", "CA", "CO", "CT")
+states <- c("AL", "AK", "AR", "AZ", "CA")
+num_districts <- setNames(c(7, 1, 9, 4, 52), states)
 races <- c("w", "b", "h", "a", "n", "o")
 parties <- c("d", "r", "i")
 voter_types <- c("registered", "likely")
 
+n <- 1000
+
 simulated_data <- data.frame(
-  "id" = sample(10000:99999, 10000, replace = FALSE),
-  "state" = sample(states, 10000, replace = TRUE),
-  "race" = sample(races, 10000, replace = TRUE, prob = c(60, 13, 19, 6, 1, 1)),
-  "party" = sample(parties, 10000, replace = TRUE, prob = c(51, 47, 2)),
-  "last_election" = sample(parties, 10000, replace = TRUE, prob = c(48, 46, 6)),
-  "voter_type" = sample(voter_types, 10000, replace = TRUE, prob = c(66, 34))
+  "id" = sample(10000:99999, n, replace = FALSE),
+  "state" = sample(states, n, replace = TRUE),
+  "race" = sample(races, n, replace = TRUE, prob = c(60, 13, 19, 6, 1, 1)),
+  "party" = sample(parties, n, replace = TRUE, prob = c(51, 47, 2)),
+  "last_election" = sample(parties, n, replace = TRUE, prob = c(48, 46, 6)),
+  "voter_type" = sample(voter_types, n, replace = TRUE, prob = c(66, 34))
 )
 
+simulated_data$district <- mapply(function(state) sample(1:num_districts[state], 1), 
+                                  simulated_data$state)
 
 #### Save data ####
-write_csv(simulated_data, "data/00-simulated_data/simulated_data.csv")
+write_csv(simulated_data, "data/simulated_data/simulated_data.csv")

### 2024-10-14 scripts/01-test_simulated_data.R
Writing unit tests for the simulated data

@@ -1,23 +1,24 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated Australian 
-  #electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Tests whether the simulated data is valid and is the required size.
+# Author: Sameeck Bhatia
+# Date: 14 October 2024
+# Contact: sameeck.bhatia@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
-  # - The `tidyverse` package must be installed and loaded
-  # - 00-simulate_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+#   - The `tidyverse` package must be installed and loaded
+#   - The `testthat` packages must be installed and loaded
+#   - 00-simulate_data.R must have been run
+# Any other information needed? None
 
 
 #### Workspace setup ####
 library(tidyverse)
+library(testthat)
 
-analysis_data <- read_csv("data/00-simulated_data/simulated_data.csv")
+simulated_data <- read_csv("data/simulated_data/simulated_data.csv")
 
 # Test if the data was successfully loaded
-if (exists("analysis_data")) {
+if (exists("simulated_data")) {
   message("Test Passed: The dataset was successfully loaded.")
 } else {
   stop("Test Failed: The dataset could not be loaded.")
@@ -25,65 +26,22 @@ if (exists("analysis_data")) {
 
 
 #### Test data ####
+test_that("The dataset has 1000 observations", {
+  expect_equal(nrow(simulated_data), 1000)
+})
 
-# Check if the dataset has 151 rows
-if (nrow(analysis_data) == 151) {
-  message("Test Passed: The dataset has 151 rows.")
-} else {
-  stop("Test Failed: The dataset does not have 151 rows.")
-}
+test_that("Each state has at least 1 congressional district and at most 52", {
+  expect_in(range(simulated_data$district), c(1, 52))
+})
 
-# Check if the dataset has 3 columns
-if (ncol(analysis_data) == 3) {
-  message("Test Passed: The dataset has 3 columns.")
-} else {
-  stop("Test Failed: The dataset does not have 3 columns.")
-}
+test_that("There are three parties in the dataset", {
+  expect_length(unique(simulated_data$party), 3)
+})
 
-# Check if all values in the 'division' column are unique
[…]

### 2024-10-20 paper/paper.qmd
Updating authors

@@
   - Sean Chua
+  - Tanmay Shinde
 thanks: "Code and data are available at: [https://github.com/SameeckBhatia/2024-US-Elections](https://github.com/SameeckBhatia/2024-US-Elections)."

### 2024-10-20 scripts/02-download_data.R
Downloading and saving the raw data

@@ -1,26 +1,21 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Downloads the data from the FiveThirtyEight website and saves it
+# Author: Sameeck Bhatia
+# Date: 20 October 2024
+# Contact: sameeck.bhatia@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites:
+#   - The `tidyverse` package must be installed and loaded
+# Any other information needed? None
 
 
 #### Workspace setup ####
-library(opendatatoronto)
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
-
+raw_data <- read_csv("https://projects.fivethirtyeight.com/polls/data/president_polls.csv")
 
 
 #### Save data ####
-# [...UPDATE THIS...]
-# change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 
-
-         
+write_csv(raw_data, "data/raw_data/raw_data.csv") 

### 2024-10-20 scripts/03-clean_data.R
Cleaning the raw data

@@ -1,44 +1,29 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans raw polling data to prepare for testing and analysis
+# Author: Sameeck Bhatia
+# Date: 20 October 2024
+# Contact: sameeck.bhatia@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites:
+#   - The `tidyverse` package must be installed and loaded
+#   - 02-download_data.R must have been run
+# Any other information needed? None
 
 #### Workspace setup ####
 library(tidyverse)
 
 #### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
+raw_data <- read_csv("data/raw_data/raw_data.csv")
 
-cleaned_data <-
-  raw_data |>
-  janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
-  mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
-  ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "6",
-                                 "60",
-                                 wing_width_mm)) |>
-  mutate(
-    wing_width_mm = as.numeric(wing_width_mm),
-    wing_length_mm = as.numeric(wing_length_mm),
-    flying_time_sec_first_timer = as.numeric(flying_time_sec_first_timer)
-  ) |>
-  rename(flying_time = flying_time_sec_first_timer,
-         width = wing_width_mm,
-         length = wing_length_mm
-         ) |> 
-  tidyr::drop_na()
+analysis_data <- raw_data |>
+                 mutate(start_date = mdy(start_date)) |>
+                 filter(candidate_name == "Donald Trump", 
+                        numeric_grade >= 2.8, 
+                        pollscore < 0, 
[…]

### 2024-10-22 scripts/02-download_data.R
Testing the analysis data

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Downloads the data from the FiveThirtyEight website and saves it
+# Purpose: Downloads the data from the FiveThirtyEight website and saves it.
 # Author: Sameeck Bhatia
 # Date: 20 October 2024
 # Contact: sameeck.bhatia@mail.utoronto.ca

### 2024-10-22 scripts/03-clean_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Cleans raw polling data to prepare for testing and analysis
+# Purpose: Cleans raw polling data to prepare for testing and analysis.
 # Author: Sameeck Bhatia
 # Date: 20 October 2024
 # Contact: sameeck.bhatia@mail.utoronto.ca

### 2024-10-22 scripts/04-test_analysis_data.R

@@ -1,69 +1,46 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests whether the analysis data is valid and has the required variables.
+# Author: Sameeck Bhatia
+# Date: 21 October 2024
+# Contact: sameeck.bhatia@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 
+#   - The `tidyverse` package must be installed and loaded
+#   - The `testthat` packages must be installed and loaded
+#   - 03-clean_data.R must have been run
+# Any other information needed? None
 
 
 #### Workspace setup ####
 library(tidyverse)
 library(testthat)
 
-data <- read_csv("data/02-analysis_data/analysis_data.csv")
+data <- read_csv("data/analysis_data/analysis_data.csv")
+
+# Test if the data was successfully loaded
+if (exists("data")) {
+  message("Test Passed: The dataset was successfully loaded.")
+} else {
+  stop("Test Failed: The dataset could not be loaded.")
+}
 
 
 #### Test data ####
-# Test that the dataset has 151 rows - there are 151 divisions in Australia
-test_that("dataset has 151 rows", {
-  expect_equal(nrow(analysis_data), 151)
+test_that("Critical fields have no missing values", {
+  expect_false(any(is.na(data$poll_id)))
+  expect_false(any(is.na(data$pollster)))
+  expect_false(any(is.na(data$pct)))
 })
 
-# Test that the dataset has 3 columns
-test_that("dataset has 3 columns", {
-  expect_equal(ncol(analysis_data), 3)
+test_that("Percentage values are within valid range", {
+  expect_true(all(data$pct >= 0 & data$pct <= 100))
 })
 
-# Test that the 'division' column is character type
-test_that("'division' is character", {
-  expect_type(analysis_data$division, "character")
+test_that("Sample sizes are positive", {
+  expect_true(all(na.omit(data$sample_size) > 0))
 })
 
-# Test that the 'party' column is character type
-test_that("'party' is character", {
-  expect_type(analysis_data$party, "character")
[…]

### 2024-10-22 scripts/06-model_data.R
Creating a model for the data

@@ -1,11 +1,14 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Models popular vote for Trump from election data.
+# Author: Sameeck Bhatia
+# Date: 21 October, 2024
+# Contact: sameeck.bhatia@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites:
+#   - The `tidyverse` package must be installed and loaded
+#   - The `rstanarm` package must be installed and loaded
+#   - 03-clean_data.R must have been run
+# Any other information needed? None
 
 
 #### Workspace setup ####
@@ -16,22 +19,23 @@ library(rstanarm)
 analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
 
 ### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+priors <- normal(0.5, 0.02, autoscale = TRUE)
+
+election_model <- stan_glm(
+  formula = pct ~ pollster + numeric_grade + pollscore + sample_size + population,
+  data = analysis_data,
+  family = gaussian(link = "identity"),
+  prior = priors,
+  prior_intercept = priors,
+  cores = 4,
+  iter = 2000,
+  adapt_delta = 0.95,
+  seed = 12
+)
 
 
 #### Save model ####
 saveRDS(
-  first_model,
-  file = "models/first_model.rds"
+  election_model,
+  file = "models/election_model.rds"
 )
-
-

### 2024-10-22 paper/paper.qmd
rough abstract and intro

--- 2024-10-13 paper/paper.qmd
@@
 date-format: long
-abstract: "Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Proin semper lobortis ante quis euismod.
-Praesent iaculis, nunc sed sagittis dignissim, metus eros venenatis nunc, in posuere risus felis eget nisi.
-Praesent pulvinar metus velit, sit amet tincidunt dolor consectetur id.
-Praesent mi nisi, venenatis nec euismod a, vehicula et nisl.
-In hac habitasse platea dictumst.
-Sed tristique ligula id suscipit convallis.
-Donec eget orci in felis consequat fringilla id sit amet lacus."
+abstract: "This paper analyzes polling data for the 2024 U.S.
+Presidential election to predict the winner, while also capturing demographic sentiment toward the two main contenders - Donald Trump and Kamala Harris.
+We found that ....[NEED TO COMPLETE].
+This study highlights that factors such as ....
+the reputation of the pollster, quality of the poll, bias, sample size, demographic area...[COME BACK AND CHANGE] are essential for analyzing polling data and thereby forecasting election outcomes.
+Highlighting these trends is crucial for understanding the evolving political landscape in the U.S., as they reveal how voter demographics and sentiments shape election outcomes."
 format: pdf
+toc: true
 number-sections: true
@@
 library(tidyverse)
-library(palmerpenguins)
 ```
@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Curabitur tincidunt nec eros ut consequat.
-Donec consectetur purus non nisl posuere, et gravida erat bibendum.
-Donec tincidunt tortor suscipit dignissim convallis.
-Pellentesque elit libero, varius a orci tincidunt, rhoncus sodales augue.
-Donec egestas, risus vitae feugiat efficitur, nunc velit euismod tellus, at dictum neque orci id nisi.
-Ut sit amet nisl suscipit, elementum nisl quis, volutpat sem.
-Phasellus mauris sapien, facilisis at eros eu, consequat gravida lorem.
-Praesent pulvinar blandit enim sed aliquam.
-Cras purus nunc, auctor ut lectus sit amet, facilisis dignissim ligula.
-Cras ligula odio, eleifend sit amet sem ut, sollicitudin imperdiet massa.
-Vivamus eget mi bibendum, vehicula ipsum a, pretium felis.
-Maecenas semper vel nisi fringilla luctus.
+\textbf{Broader Context + What the Paper is About} As the 2024 U.S.
+Presidential election draws near, the race between former President Donald Trump and Vice President Kamala Harris has garnered widespread attention worldwide.
+With both candidates representing contrasting ideologies and policy priorities, appealing to distinct voter bases, understanding the public sentiment surrounding them becomes crucial in predicting the election's outcome.
+Polls and demographic analyses provide a lens through which we can examine the factors influencing voter preferences and gauge the political landscape as it evolves.
+This paper aims to analyze the 2024 election polling data to not only forecast the winner but also to capture the demographic-wise public sentiment surrounding the two contenders.
 
-Donec eleifend tortor eu diam convallis, eu dictum nunc tincidunt.
-Nunc consectetur sapien arcu, id gravida arcu pulvinar id.
-Nam dignissim nisl ac ornare maximus.
-Nullam eget vulputate libero.
-Vestibulum vitae sapien risus.
-Vivamus facilisis orci semper, tincidunt massa at, faucibus sem.
-Ut ac augue elementum, bibendum justo ornare, porta tortor.
-Vestibulum vitae turpis orci.
-Sed ultrices ante metus, vel efficitur eros feugiat luctus.
-Nulla at tincidunt nunc, et dapibus nisi.
-Proin feugiat, elit pellentesque lobortis pellentesque, magna odio efficitur diam, eget finibus arcu tortor sit amet diam.
-Duis malesuada lacus sit amet dui auctor pellentesque.
-Sed fermentum lectus id vulputate euismod.
-Duis ultrices magna eu leo consequat consectetur.
-Nulla facilisi.
+\textbf{Estimand:} The primary estimand for this analysis is the predicted support percentage for each of the two candidates.
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Curabitur tincidunt nec eros ut consequat.
-Donec consectetur purus non nisl posuere, et gravida erat bibendum.
-Donec tincidunt tortor suscipit dignissim convallis.
-Pellentesque elit libero, varius a orci tincidunt, rhoncus sodales augue.
-Donec egestas, risus vitae feugiat efficitur, nunc velit euismod tellus, at dictum neque orci id nisi.
-Ut sit amet nisl suscipit, elementum nisl quis, volutpat sem.
-Phasellus mauris sapien, facilisis at eros eu, consequat gravida lorem.
-Praesent pulvinar blandit enim sed aliquam.
-Cras purus nunc, auctor ut lectus sit amet, facilisis dignissim ligula.
-Cras ligula odio, eleifend sit amet sem ut, sollicitudin imperdiet massa.
-Vivamus eget mi bibendum, vehicula ipsum a, pretium felis.
-Maecenas semper vel nisi fringilla luctus.
+\textbf{What was done:} We used polling data from FiveThirtyEight, which includes surveys from organizations such as YouGov, Siena/NYT, and Washington Post.
+We used a Bayesian approach to model the polling support percentages for both candidates, and understand how polling factors such as numeric grade, poll score, state, and sample size affect the predicted support percentage.
 
-Donec eleifend tortor eu diam convallis, eu dictum nunc tincidunt.
-Nunc consectetur sapien arcu, id gravida arcu pulvinar id.
-Nam dignissim nisl ac ornare maximus.
-Nullam eget vulputate libero.
-Vestibulum vitae sapien risus.
-Vivamus facilisis orci semper, tincidunt massa at, faucibus sem.
-Ut ac augue elementum, bibendum justo ornare, porta tortor.
-Vestibulum vitae turpis orci.
-Sed ultrices ante metus, vel efficitur eros feugiat luctus.
-Nulla at tincidunt nunc, et dapibus nisi.
-Proin feugiat, elit pellentesque lobortis pellentesque, magna odio efficitur diam, eget finibus arcu tortor sit amet diam.
-Duis malesuada lacus sit amet dui auctor pellentesque.
-Sed fermentum lectus id vulputate euismod.
-Duis ultrices magna eu leo consequat consectetur.
-Nulla facilisi.
+The results show that ... [TO-DO]. These results are important because ... [TO-DO].
+
+The rest of the paper is structured as follows: @sec-data details the data and measurement process.@sec-model presents the model and justifies the choices made in the building of the chosen model.
+@sec-results presents the results, highlighting the relationship between different variables and the polling support percentage, and @sec-discussion discusses the implications of the findings for this as well as future election forecasting.
 
@@
 
-# Model
+# Model {#sec-model}
 
@@
 
-# Results
+# Results {#sec-results}
 
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 

### 2024-10-22 scripts/cleaning.R
Cleaning up the repo structure and files

@@ -6,7 +6,7 @@
 # License: MIT
 # Pre-requisites:
 #   - The `tidyverse` package must be installed and loaded
-#   - 02-download_data.R must have been run
+#   - gather.R must have been run
 # Any other information needed? None
 
 #### Workspace setup ####

### 2024-10-22 scripts/modeling.R

@@ -7,7 +7,7 @@
 # Pre-requisites:
 #   - The `tidyverse` package must be installed and loaded
 #   - The `rstanarm` package must be installed and loaded
-#   - 03-clean_data.R must have been run
+#   - cleaning.R must have been run
 # Any other information needed? None
 
 

### 2024-10-22 scripts/test_analysis.R

@@ -7,7 +7,7 @@
 # Pre-requisites: 
 #   - The `tidyverse` package must be installed and loaded
 #   - The `testthat` packages must be installed and loaded
-#   - 03-clean_data.R must have been run
+#   - cleaning.R must have been run
 # Any other information needed? None
 
 

### 2024-10-22 scripts/test_simulation.R

@@ -7,7 +7,7 @@
 # Pre-requisites: 
 #   - The `tidyverse` package must be installed and loaded
 #   - The `testthat` packages must be installed and loaded
-#   - 00-simulate_data.R must have been run
+#   - simulation.R must have been run
 # Any other information needed? None
 
 

### 2024-10-22 scripts/modeling.R
Updating the prior of the model

@@ -19,12 +19,12 @@ library(rstanarm)
 analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
 
 ### Model data ####
-priors <- normal(0.5, 0.02, autoscale = TRUE)
+priors <- normal(50, 2)
 
 election_model <- stan_glm(
   formula = pct ~ pollster + numeric_grade + pollscore + sample_size + population,
   data = analysis_data,
-  family = gaussian(link = "identity"),
+  family = gaussian(),
   prior = priors,
   prior_intercept = priors,
   cores = 4,

### 2024-10-22 scripts/cleaning.R
Updating the model

@@ -20,7 +20,8 @@ analysis_data <- raw_data |>
                  filter(candidate_name == "Donald Trump", 
                         numeric_grade >= 2.8, 
                         pollscore < 0, 
-                        start_date >= as.Date("2024-07-21")) |>
+                        start_date >= as.Date("2024-07-21"),
+                        pollster %in% c("Emerson", "Siena/NYT", "YouGov")) |>
                  select(poll_id, pollster, numeric_grade, pollscore, methodology,
                         state, start_date, end_date, sample_size, population, 
                         election_date, party, answer, candidate_name, pct) 

### 2024-10-22 paper/paper.qmd

@@
 We found that ....[NEED TO COMPLETE].
-This study highlights that factors such as ....
-the reputation of the pollster, quality of the poll, bias, sample size, demographic area...[COME BACK AND CHANGE] are essential for analyzing polling data and thereby forecasting election outcomes.
+This study highlights that considering factors such as the reputation of the pollster, quality of the poll, bias, sample size, and demographic area are essential for analyzing polling data and thereby forecasting election outcomes.
 Highlighting these trends is crucial for understanding the evolving political landscape in the U.S., as they reveal how voter demographics and sentiments shape election outcomes."
@@
 
-\textbf{Broader Context + What the Paper is About} As the 2024 U.S.
+As the 2024 U.S.
 Presidential election draws near, the race between former President Donald Trump and Vice President Kamala Harris has garnered widespread attention worldwide.
@@
 
-\textbf{Estimand:} The primary estimand for this analysis is the predicted support percentage for each of the two candidates.
+The primary estimand for this analysis is the predicted support percentage for each of the two candidates, which represents the proportion of the electorate that is expected to favor one candidate over the other.
+This estimand will be calculated based on survey data or polling results, and it will allow us to estimate the level of support each candidate has within the population.
+This analysis will also provide insights into how various demographic factors or voter preferences may influence the final outcomes.
 
-\textbf{What was done:} We used polling data from FiveThirtyEight, which includes surveys from organizations such as YouGov, Siena/NYT, and Washington Post.
+We use polling data from FiveThirtyEight, focusing on surveys from organizations such as YouGov, Siena/NYT, and Washington Post.
 We used a Bayesian approach to model the polling support percentages for both candidates, and understand how polling factors such as numeric grade, poll score, state, and sample size affect the predicted support percentage.
@@
 
-The rest of the paper is structured as follows: @sec-data details the data and measurement process.@sec-model presents the model and justifies the choices made in the building of the chosen model.
+The rest of the paper is structured as follows: @sec-data details the data and measurement process.
+@sec-model presents the model and justifies the choices made in the building of the chosen model.
 @sec-results presents the results, highlighting the relationship between different variables and the polling support percentage, and @sec-discussion discusses the implications of the findings for this as well as future election forecasting.
@@
 
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
+The dataset used for this paper is the 2024 national-level presidential general election dataset from FiveThirtyEight [@FiveThirtyEight], which compiles polling data from various reputable pollsters, including YouGov, Siena/NYT, Ipsos, and more.
+This dataset offers a comprehensive snapshot of public opinion leading up to the 2024 U.S.
+Presidential election, capturing support for the two main contenders: Donald Trump and Kamala Harris.
+By focusing on national polling, this dataset provides insight into voter sentiment across a wide range of demographic groups and regions.
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
-Mauris non libero vel ligula tincidunt consequat.
-Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
-Vivamus feugiat et quam ut consequat.
-Aenean mollis ullamcorper facilisis.
-Vivamus scelerisque lectus et elementum vulputate.
-Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
-Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
-Curabitur vitae tortor nec ligula scelerisque rutrum.
-Nullam feugiat odio metus.
-Cras id convallis ante, ut ornare velit.
-Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
+The FiveThirtyEight dataset is part of a broader landscape of polling data used in electoral predictions.
+It includes surveys conducted at the national level, focusing on general election matchups, and is continuously updated as new polls are released.
+The dataset covers polls taken from early in the election cycle to the final days before the election, capturing the shifts in public opinion over time.
+While there are other polling datasets available, such as those from RealClearPolitics [@RealClearPolitics] or individual pollsters, we selected the FiveThirtyEight dataset due to its high level of transparency, detailed methodology grades for each pollster, and advanced polling aggregation techniques, which adjust for biases and historical pollster performance.
+These features provide a more refined and reliable dataset compared to others that might not incorporate such rigorous adjustments.
+
+We use the statistical programming language R [@citeR] to perform data cleaning and analysis on the dataset to ensure consistency and reliability.
+Polls were filtered to include only those related to Donald Trump and Kamala Harris, with a pollster grade of 2.8 or higher, and those with a negative pollscore, ensuring reliability and unbiasedness.
+The dataset was further narrowed by selecting polls conducted on or after July 21, 2024, to focus on the shift in sentiment over time after the Democratic Party announced Harris as their nominee for president in the 2024 elections.
 
@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
-Mauris non libero vel ligula tincidunt consequat.
-Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
-Vivamus feugiat et quam ut consequat.
-Aenean mollis ullamcorper facilisis.
-Vivamus scelerisque lectus et elementum vulputate.
-Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
-Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
-Curabitur vitae tortor nec ligula scelerisque rutrum.
-Nullam feugiat odio metus.
-Cras id convallis ante, ut ornare velit.
-Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
+The process of converting real-world electoral phenomena into data involves careful measurement of public sentiment toward presidential candidates, in the context of the 2024 U.S.
+presidential election.
+The dataset is built from polling data collected by various established pollsters, such as YouGov and Siena/NYT, who use a variety of survey techniques to measure voter preferences.
+These polls aim to capture critical variables that reflect voter sentiment, such as the percentage of respondents favoring each candidate, the sample size of the poll, and the demographics of the voters surveyed.
+
+The measurement begins with pollsters designing surveys aimed at accurately reflecting voter behavior and sentiment.
+A subset of the population is sampled using stratified random sampling to ensure that the sample accurately represents the diverse demographic makeup of the electorate.
+Responses are collected through various channels, including phone calls, online surveys, and face-to-face interviews.
+These polls capture voter sentiment around a candidate as the percentage of respondents favoring the candidate.
+
+Once the polling is done, the dataset undergoes extensive cleaning and processing to handle missing values and any discrepancies in the data.
+Each row in the dataset represents the outcome of a poll, including details such as the date it was conducted, the pollster's methodology, and the percentage of support for each candidate.
+Platforms like FiveThirtyEight then assign a numeric grade and poll score to each poll to evaluate the reliability, quality, and historical accuracy of their polling methods.
+The numeric grade is a standardized rating assigned to pollsters based on their historical performance, transparency, and polling methodology.
+The poll score measures the accuracy, consistency, and bias in each poll, pollsters that show bias toward a particular party receive a positive score.
+
+Thus, each entry in the dataset corresponds to the results of a specific poll, providing information on when it was conducted, the pollster's methodology, and key metrics such as biasdness, sample size, and geographic coverage.
+By converting complex voter opinions into structured data, we are able to systematically analyze trends in public sentiment, making it possible to predict the election’s outcome with greater precision.
 
@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
-Mauris non libero vel ligula tincidunt consequat.
-Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
-Vivamus feugiat et quam ut consequat.
-Aenean mollis ullamcorper facilisis.
-Vivamus scelerisque lectus et elementum vulputate.
-Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
-Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
-Curabitur vitae tortor nec ligula scelerisque rutrum.
-Nullam feugiat odio metus.
-Cras id convallis ante, ut ornare velit.
-Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
+TO-DO: All variables should be thoroughly examined and explained.
+
+TO-DO: It is important to understand what the variables look like by including graphs, and possibly tables, of all observations, along with discussion of those graphs and the other features of these data.
+Summary statistics should also be included, and well as any relationships between the variables.
 

### 2024-10-22 scripts/cleaning.R
changed format of analysis_data file to store it as a parquet file

@@ -11,6 +11,7 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(arrow)
 
 #### Clean data ####
 raw_data <- read_csv("data/raw_data/raw_data.csv")
@@ -26,5 +27,5 @@ analysis_data <- raw_data |>
                         state, start_date, end_date, sample_size, population, 
                         election_date, party, answer, candidate_name, pct) 
 
-#### Save data ####
-write_csv(analysis_data, "data/analysis_data/analysis_data.csv")
+#### Save data as parquet file ####
+write_parquet(x = analysis_data, sink = "data/analysis_data/analysis_data.parquet")

### 2024-10-22 scripts/cleaning.R
Changing how the analysis data is read

@@ -6,6 +6,7 @@
 # License: MIT
 # Pre-requisites:
 #   - The `tidyverse` package must be installed and loaded
+#   - The `arrow` package must be installed and loaded
 #   - gather.R must have been run
 # Any other information needed? None
 

### 2024-10-22 scripts/modeling.R

@@ -7,6 +7,7 @@
 # Pre-requisites:
 #   - The `tidyverse` package must be installed and loaded
 #   - The `rstanarm` package must be installed and loaded
+#   - The `arrow` package must be installed and loaded
 #   - cleaning.R must have been run
 # Any other information needed? None
 
@@ -14,9 +15,10 @@
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
+library(arrow)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
 
 ### Model data ####
 priors <- normal(50, 2)

### 2024-10-22 paper.qmd
Add files via upload

---
title: "Race to the Ballot Box: Will Demographics Decide a Winner This Year?"
subtitle: "A Regressional Approach to Race and Political Preferences in the 2024 US Elections and Insights on the Next"
author: 
  - Sameeck Bhatia
  - Sean Chua
thanks: "Code and data are available at: [https://github.com/SameeckBhatia/2024-US-Elections](https://github.com/SameeckBhatia/2024-US-Elections)."
date: today
date-format: long
abstract: "Lorem ipsum dolor sit amet, consectetur adipiscing elit. Proin semper lobortis ante quis euismod. Praesent iaculis, nunc sed sagittis dignissim, metus eros venenatis nunc, in posuere risus felis eget nisi. Praesent pulvinar metus velit, sit amet tincidunt dolor consectetur id. Praesent mi nisi, venenatis nec euismod a, vehicula et nisl. In hac habitasse platea dictumst. Sed tristique ligula id suscipit convallis. Donec eget orci in felis consequat fringilla id sit amet lacus."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur tincidunt nec eros ut consequat. Donec consectetur purus non nisl posuere, et gravida erat bibendum. Donec tincidunt tortor suscipit dignissim convallis. Pellentesque elit libero, varius a orci tincidunt, rhoncus sodales augue. Donec egestas, risus vitae feugiat efficitur, nunc velit euismod tellus, at dictum neque orci id nisi. Ut sit amet nisl suscipit, elementum nisl quis, volutpat sem. Phasellus mauris sapien, facilisis at eros eu, consequat gravida lorem. Praesent pulvinar blandit enim sed aliquam. Cras purus nunc, auctor ut lectus sit amet, facilisis dignissim ligula. Cras ligula odio, eleifend sit amet sem ut, sollicitudin imperdiet massa. Vivamus eget mi bibendum, vehicula ipsum a, pretium felis. Maecenas semper vel nisi fringilla luctus.

Donec eleifend tortor eu diam convallis, eu dictum nunc tincidunt. Nunc consectetur sapien arcu, id gravida arcu pulvinar id. Nam dignissim nisl ac ornare maximus. Nullam eget vulputate libero. Vestibulum vitae sapien risus. Vivamus facilisis orci semper, tincidunt massa at, faucibus sem. Ut ac augue elementum, bibendum justo ornare, porta tortor. Vestibulum vitae turpis orci. Sed ultrices ante metus, vel efficitur eros feugiat luctus. Nulla at tincidunt nunc, et dapibus nisi. Proin feugiat, elit pellentesque lobortis pellentesque, magna odio efficitur diam, eget finibus arcu tortor sit amet diam. Duis malesuada lacus sit amet dui auctor pellentesque. Sed fermentum lectus id vulputate euismod. Duis ultrices magna eu leo consequat consectetur. Nulla facilisi.

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur tincidunt nec eros ut consequat. Donec consectetur purus non nisl posuere, et gravida erat bibendum. Donec tincidunt tortor suscipit dignissim convallis. Pellentesque elit libero, varius a orci tincidunt, rhoncus sodales augue. Donec egestas, risus vitae feugiat efficitur, nunc velit euismod tellus, at dictum neque orci id nisi. Ut sit amet nisl suscipit, elementum nisl quis, volutpat sem. Phasellus mauris sapien, facilisis at eros eu, consequat gravida lorem. Praesent pulvinar blandit enim sed aliquam. Cras purus nunc, auctor ut lectus sit amet, facilisis dignissim ligula. Cras ligula odio, eleifend sit amet sem ut, sollicitudin imperdiet massa. Vivamus eget mi bibendum, vehicula ipsum a, pretium felis. Maecenas semper vel nisi fringilla luctus.

Donec eleifend tortor eu diam convallis, eu dictum nunc tincidunt. Nunc consectetur sapien arcu, id gravida arcu pulvinar id. Nam dignissim nisl ac ornare maximus. Nullam eget vulputate libero. Vestibulum vitae sapien risus. Vivamus facilisis orci semper, tincidunt massa at, faucibus sem. Ut ac augue elementum, bibendum justo ornare, porta tortor. Vestibulum vitae turpis orci. Sed ultrices ante metus, vel efficitur eros feugiat luctus. Nulla at tincidunt nunc, et dapibus nisi. Proin feugiat, elit pellentesque lobortis pellentesque, magna odio efficitur diam, eget finibus arcu tortor sit amet diam. Duis malesuada lacus sit amet dui auctor pellentesque. Sed fermentum lectus id vulputate euismod. Duis ultrices magna eu leo consequat consectetur. Nulla facilisi.

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

## Measurement

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

## Outcome variables

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

## Predictor variables

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

# Model

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum.

## Model set-up

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

# Results

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

# Discussion

## First discussion point {#sec-first-point}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

## Second discussion point

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

## Third discussion point

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

## Weaknesses and next steps

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod. Mauris non libero vel ligula tincidunt consequat. Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus. Vivamus feugiat et quam ut consequat. Aenean mollis ullamcorper facilisis. Vivamus scelerisque lectus et elementum vulputate. Nulla et arcu vehicula, iaculis felis sit amet, semper justo. Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem. Curabitur vitae tortor nec ligula scelerisque rutrum. Nullam feugiat odio metus. Cras id convallis ante, ut ornare velit. Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.

\newpage

\appendix

# Appendix {.unnumbered}
The poll was conducted from Sept. 29 to Oct. 6 and surveyed 3,385 likely voters nationwide and found that Harris led Trump by 49 percent to 46 percent, a slight lead that is within the poll’s margin of error (2.4 points). According to [@nyt-crosstabs], the national poll includes separate polls of 622 voters in Florida, and 617 voters in Texas. The weight given to each of these groups in the national poll has been adjusted so that the overall results are reflective of the entire country. Polls were also conducted by telephone, using live interviewers, in both English and Spanish, with about 98% of respondents were contacted on a cellphone [@nyt-topline]. For battleground polls, voters were called from Arizona, Georgia, Michigan, Nevada, Pennsylvania and Wisconsin [@nyt-methodology] — swing states that have a significant share in electoral college votes). In light of this, responses were also weighted to consider over- and under-represented voters to ensure that each demographic is adequately represented.

This poll employs a random sampling approach of registered voters using telephone interviews, with a focus on both landlines and cellphones. As such, this generally allowed for a representative sample. In addition, NYT/Siena also used voter registration files help ensure proper balance between political parties, and telephone polls have historically proven to be effective in gauging public opinion from recent elections. However, one particular drawback is that telephone response rates are extremely low; in fact, for this poll, “fewer than 2% of contacted individuals participate in the survey.”

In handling non-responses within their questionnaire, for some questions another “sub-question” related to the original is asked only once in order to get a definitive answer; this usually occurs in questions related to leaning (not outright) candidate support. By doing this, it allows NYT to more accurately gauge the public’s opinions. However, at times, they leave non-responses as “Refused” or “Don’t know” often on questions targeted to the individual person (e.g. How has ___ affected you personally?). At this point, there is little no use prodding further in case of a non-response. The overall questionnaire is of high quality (NYT/Siena is one of the most reputable polls after all), and it has its strong and weak points. First, most questions, often those on respondent identification or demographic, are unbiased and fair; in particular, questions on candidate preferences did not contain words suggestive of one candidate over another. However, some questions contain gender-coded language that may skew respondents’ answers in favor of one candidate (e.g. In the question “cares more about people like you” the word “cares” is more often associated with females and so respondents are more likely to choose Harris as the answer, which was seen in the poll results with Harris receiving 49% of responses versus Trump’s 41%).

\newpage

# References

### 2024-10-22 paper/paper.qmd
added pollster overview and evaluation

@@
 
-# Appendix {.unnumbered}
+# Appendix {-}
+
+# Additional Data Details
+
+# Additional Model Details
+
+# Polling Methodology Overview and Evaluation for Siena/NYT
+
+The poll was conducted from Sept.
+29 to Oct.
+6 and surveyed 3,385 likely voters nationwide and found that Harris led Trump by 49 percent to 46 percent, a slight lead that is within the poll’s margin of error (2.4 points).
+According to [@nyt-crosstabs], the national poll includes separate polls of 622 voters in Florida, and 617 voters in Texas.
+The weight given to each of these groups in the national poll has been adjusted so that the overall results are reflective of the entire country.
+Polls were also conducted by telephone, using live interviewers, in both English and Spanish, with about 98% of respondents were contacted on a cellphone [@nyt-topline].
+For battleground polls, voters were called from Arizona, Georgia, Michigan, Nevada, Pennsylvania and Wisconsin [@nyt-methodology] — swing states that have a significant share in electoral college votes).
+In light of this, responses were also weighted to consider over- and under-represented voters to ensure that each demographic is adequately represented.
+
+This poll employs a random sampling approach of registered voters using telephone interviews, with a focus on both landlines and cellphones.
+As such, this generally allowed for a representative sample.
+In addition, NYT/Siena also used voter registration files help ensure proper balance between political parties, and telephone polls have historically proven to be effective in gauging public opinion from recent elections.
+However, one particular drawback is that telephone response rates are extremely low; in fact, for this poll, “fewer than 2% of contacted individuals participate in the survey.”
+
+In handling non-responses within their questionnaire, for some questions another “sub-question” related to the original is asked only once in order to get a definitive answer; this usually occurs in questions related to leaning (not outright) candidate support.
+By doing this, it allows NYT to more accurately gauge the public’s opinions.
+However, at times, they leave non-responses as “Refused” or “Don’t know” often on questions targeted to the individual person (e.g.
+How has ___ affected you personally?).
+At this point, there is little no use prodding further in case of a non-response.
+The overall questionnaire is of high quality (NYT/Siena is one of the most reputable polls after all), and it has its strong and weak points.
+First, most questions, often those on respondent identification or demographic, are unbiased and fair; in particular, questions on candidate preferences did not contain words suggestive of one candidate over another.
+However, some questions contain gender-coded language that may skew respondents’ answers in favor of one candidate (e.g.
+In the question “cares more about people like you” the word “cares” is more often associated with females and so respondents are more likely to choose Harris as the answer, which was seen in the poll results with Harris receiving 49% of responses versus Trump’s 41%).
+
+# Idealized Methodology
+
+## Sampling Approach
+
+## Data Validation
 

### 2024-10-22 paper/paper.qmd
Updating the paper and adding references

@@
 
+In predicting U.S.
+presidential election outcomes through polling, an ideal methodology would utilize stratified sampling to ensure a representative sample of the electorate.
+This approach would survey registered voters from all states, then the sample will be adjusted proportionally, reflecting key demographic factors such as education, race, gender, and the urban-to-rural population ratio.
+To achieve this, voter registration records and census data would serve as the basis for selecting respondents.
+Telephone polling would be employed, with calls made at different times of the day to mitigate potential biases from non-response patterns, as certain groups of individuals may be more reachable at specific times.
+Given that modern telephone polling often encounters low response rates, this methodology assumes a 10% response rate, consistent with findings, highlighting the challenges in obtaining representative samples from telephone-based surveys [@keeter].
+Therefore, around 15,000 individuals will be contacted to obtain a desired sample size of 1500.
+Despite the low response rate, carefully deploying methods should help mitigate biases and improve the accuracy of election predictions.
+
+The survey will begin by introducing each potential participant to the topic and providing necessary context about the purpose of the research.
+This introduction aims to make the participants feel informed and comfortable with the process.
+The first question will ask whether the individual is willing to participate in the survey, emphasizing that participation is voluntary.
+It will also be clearly communicated that respondents may drop out of the survey at any point if they choose.
+Once participants agree, they will proceed to answer a series of demographic questions that will help ensure a diverse and stratified sample.
+These questions include:
+
+- "What is your gender?"
+- "What is your age?"
+- "Which city do you live in?"
+- "What race do you identify as?"
+- "What is your highest degree of education?"
+- "Will you be voting in the upcoming election?"
+- "Which candidate will you be voting for?"
+
 ## Data Validation

### 2024-10-29 scripts/cleaning.R
Updating the cleaned data and the model

@@ -18,15 +18,19 @@ library(arrow)
 raw_data <- read_csv("data/raw_data/raw_data.csv")
 
 analysis_data <- raw_data |>
-                 mutate(start_date = mdy(start_date)) |>
-                 filter(candidate_name == "Donald Trump", 
-                        numeric_grade >= 2.8, 
-                        pollscore < 0, 
-                        start_date >= as.Date("2024-07-21"),
-                        pollster %in% c("Emerson", "Siena/NYT", "YouGov")) |>
-                 select(poll_id, pollster, numeric_grade, pollscore, methodology,
-                        state, start_date, end_date, sample_size, population, 
-                        election_date, party, answer, candidate_name, pct) 
+                 mutate(start_date = mdy(start_date), 
+                        candidate_trump = ifelse(candidate_name == "Donald Trump", 1, 0),
+                        swing_state = ifelse(state %in% c("Arizona", "Georgia", "Michigan", 
+                                                          "Nevada", "North Carolina", 
+                                                          "Pennsylvania", "Wisconsin"), 1, 0)) |>
+                 filter(start_date >= as.Date("2024-07-21"),
+                        party %in% c("DEM", "REP"), 
+                        pollster %in% c("Emerson", "Siena/NYT", "YouGov"),
+                        swing_state == 1) |>
+                 select(poll_id, pollster, numeric_grade, state,start_date, 
+                        end_date, sample_size, population, election_date, party, 
+                        answer, candidate_name, pct, candidate_trump) |>
+                 drop_na()
 
 #### Save data as parquet file ####
 write_parquet(x = analysis_data, sink = "data/analysis_data/analysis_data.parquet")

### 2024-10-29 scripts/modeling.R

@@ -16,25 +16,43 @@
 library(tidyverse)
 library(rstanarm)
 library(arrow)
+library(caret)
 
-#### Read data ####
-analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
+analysis_data <- read_parquet("analysis_data.parquet")
 
-### Model data ####
-priors <- normal(50, 2)
+model_data <- analysis_data |> 
+  select(pollster, numeric_grade, state, sample_size, pct, candidate_trump) |>
+  mutate(pollster = as.factor(pollster),
+         state = as.factor(state),
+         weight = numeric_grade * (sample_size / min(sample_size)))
 
-election_model <- stan_glm(
-  formula = pct ~ pollster + numeric_grade + pollscore + sample_size + population,
-  data = analysis_data,
-  family = gaussian(),
+set.seed(12)
+training_index <- createDataPartition(model_data$candidate_trump, p = 0.7, list = FALSE)
+
+training_data <- model_data[training_index,]
+testing_data <- model_data[-training_index,]
+
+priors <- normal(0.5, 2.5, autoscale = TRUE)
+formula <- candidate_trump ~ (1 | pollster) + (1 | state) + sample_size + pct
+
+model <- stan_glmer(
+  formula = formula,
+  data = training_data,
+  family = binomial(link = "logit"),
   prior = priors,
   prior_intercept = priors,
+  weights = weight,
   cores = 4,
   iter = 2000,
   adapt_delta = 0.95,
-  seed = 12
 )
 
+pp_check(model)
+
+testing_data |> 
+  mutate(predicted_prob = 
+           posterior_predict(model, newdata = testing_data, draws = 1) %>% rowMeans()) |>
+  select(pollster, state, pct, candidate_trump, predicted_prob)
 
 #### Save model ####
 saveRDS(

### 2024-10-30 scripts/cleaning.R
Updating the cleaned data and the model

@@ -18,14 +18,16 @@ library(arrow)
 raw_data <- read_csv("data/raw_data/raw_data.csv")
 
 analysis_data <- raw_data |>
-                 mutate(start_date = mdy(start_date), 
+                 mutate(start_date = mdy(start_date),
+                        end_date = mdy(end_date),
+                        election_date = mdy(election_date),
                         candidate_trump = ifelse(candidate_name == "Donald Trump", 1, 0),
                         swing_state = ifelse(state %in% c("Arizona", "Georgia", "Michigan", 
                                                           "Nevada", "North Carolina", 
                                                           "Pennsylvania", "Wisconsin"), 1, 0)) |>
                  filter(start_date >= as.Date("2024-07-21"),
                         party %in% c("DEM", "REP"), 
-                        pollster %in% c("Emerson", "Siena/NYT", "YouGov"),
+                        numeric_grade >= 2.6,
                         swing_state == 1) |>
                  select(poll_id, pollster, numeric_grade, state,start_date, 
                         end_date, sample_size, population, election_date, party, 

### 2024-10-30 scripts/modeling.R

@@ -17,23 +17,28 @@ library(tidyverse)
 library(rstanarm)
 library(arrow)
 library(caret)
+library(MLmetrics)
 
-analysis_data <- read_parquet("analysis_data.parquet")
+model_data <- read_parquet("data/analysis_data/analysis_data.parquet")
 
-model_data <- analysis_data |> 
-  select(pollster, numeric_grade, state, sample_size, pct, candidate_trump) |>
+model_data <- model_data |>
   mutate(pollster = as.factor(pollster),
          state = as.factor(state),
-         weight = numeric_grade * (sample_size / min(sample_size)))
+         population = as.factor(population),
+         weight = numeric_grade * (sample_size / min(sample_size)),
+         days_to_election = as.numeric(election_date - end_date))
 
 set.seed(12)
-training_index <- createDataPartition(model_data$candidate_trump, p = 0.7, list = FALSE)
+
+training_index <- createDataPartition(model_data$state, p = 0.7, list = FALSE)
 
 training_data <- model_data[training_index,]
 testing_data <- model_data[-training_index,]
 
+testing_data <- testing_data |> filter(pollster %in% unique(training_data$pollster))
+
 priors <- normal(0.5, 2.5, autoscale = TRUE)
-formula <- candidate_trump ~ (1 | pollster) + (1 | state) + sample_size + pct
+formula <- candidate_trump ~ (1 | pollster) + (1 | state) + sample_size + pct + days_to_election
 
 model <- stan_glmer(
   formula = formula,
@@ -45,14 +50,29 @@ model <- stan_glmer(
   cores = 4,
   iter = 2000,
   adapt_delta = 0.95,
+  seed = 12
 )
 
 pp_check(model)
 
-testing_data |> 
-  mutate(predicted_prob = 
-           posterior_predict(model, newdata = testing_data, draws = 1) %>% rowMeans()) |>
-  select(pollster, state, pct, candidate_trump, predicted_prob)
+set.seed(12)
+
+predicted_data <- testing_data |>
+  select(pollster, state, candidate_trump, pct) |>
+  mutate(predicted_pct =  100 * posterior_predict(model, newdata = testing_data, 
+                                                  draws = 2000, type = "response") |> colMeans(),
+         winner_trump = ifelse(predicted_pct > 50, 1, 0))
+
+predicted_data |>
+  group_by(state) |> 
+  summarise(mean_pct = round(mean(pct), 2), 
[…]

### 2024-10-30 paper/paper.qmd
Made more changes to paper

@@
 ## Outcome variables
+We aim to predict our response variable `candidate_trump`, which is a binary variable with 0 and 1 representing a loss and win in a state respectively.
+The plot of our outcome variables is shown below:
+```{r}
 
-TO-DO: All variables should be thoroughly examined and explained.
+```
 
@@
 TO-DO: All variables should be thoroughly examined and explained.
-
-TO-DO: It is important to understand what the variables look like by including graphs, and possibly tables, of all observations, along with discussion of those graphs and the other features of these data.
-Summary statistics should also be included, and well as any relationships between the variables.
+[PLOTS OF PREDICTOR VARIABLES NEEDED]
+- **Sample Size (`sample_size`)**: The number of respondents in the poll.
+- **State (`state`)**: A categorical variable for different U.S. states.
+- **Days to Election (`days_to_election`)**: Counts the number of days until Election Day starting from today’s date (it also uses `end_date` from the original dataset).
+- **Voter Percentage of Candidate (`pct`)**: A continuous variable for the percentage of voters who plan to vote for Trump based on polling data.
 
@@
 ## Model set-up
+A Bayesian approach is used in constructing our model. As such, an informative prior is assumed, and logistic regression is implemented due to the nature of the outcome variable (binary).
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
-Mauris non libero vel ligula tincidunt consequat.
-Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
-Vivamus feugiat et quam ut consequat.
-Aenean mollis ullamcorper facilisis.
-Vivamus scelerisque lectus et elementum vulputate.
-Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
-Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
-Curabitur vitae tortor nec ligula scelerisque rutrum.
-Nullam feugiat odio metus.
-Cras id convallis ante, ut ornare velit.
-Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
+The predictor variables used in the model are as follows:
+
+- **Sample Size (`sample_size`)**: The number of respondents in the poll.
+- **State (`state`)**: A categorical variable for different U.S. states.
+- **Days to Election (`days_to_election`)**: Counts the number of days until Election Day starting from today’s date (it also uses `end_date` from the original dataset).
+- **Voter Percentage of Candidate (`pct`)**: A continuous variable for the percentage of voters who plan to vote for Trump based on polling data.
+
+The model takes the form of the following equation [TO-DO]:
+\begin{align}
+\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{transparency\_score}_i \\
+             &\quad + \beta_3 \cdot \text{sample\_size}_i + \beta_4 \cdot \text{state}_i + \beta_5 \cdot \text{end\_date}_i + \epsilon_i \\
+\epsilon_i &\sim \text{Normal}(0, \sigma^2)
+\end{align}
+
+Where: 
+\begin{align}
+\beta_0 & \text{ is the intercept term} \\
+\beta_1, \beta_2, \beta_3, \beta_4, \beta_5 & \text{ are the coefficients for each predictor} \\
+\sigma^2 & \text{ is the variance of the error term}
+\end{align}
+
+## Interpretation
+[WORDS TO-DO]
+
+## Model Justification and Evaluation
+[tbl-summary] shows the summary table for the model. 
+F1-Score blabla
 
 # Results {#sec-results}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
-Mauris non libero vel ligula tincidunt consequat.
-Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
-Vivamus feugiat et quam ut consequat.
-Aenean mollis ullamcorper facilisis.
-Vivamus scelerisque lectus et elementum vulputate.
-Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
-Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
-Curabitur vitae tortor nec ligula scelerisque rutrum.
-Nullam feugiat odio metus.
-Cras id convallis ante, ut ornare velit.
-Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
-Mauris non libero vel ligula tincidunt consequat.
-Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
-Vivamus feugiat et quam ut consequat.
-Aenean mollis ullamcorper facilisis.
-Vivamus scelerisque lectus et elementum vulputate.
-Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
-Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
-Curabitur vitae tortor nec ligula scelerisque rutrum.
-Nullam feugiat odio metus.
-Cras id convallis ante, ut ornare velit.
-Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
+[WORDS]
 
@@
 
-# Idealized Methodology
+# Appendix B: Idealized Methodology and Survey
 
-## Sampling Approach
+## Sampling Approach and Strategy
 
@@
 
+### Stratification Variables [TO-DO]
+* **Age Groups**: 18-29, 30-44, 45-64, 65+ 
+* **Gender**: Male, Female, Non-binary/Other 
+* **Race/Ethnicity**: White, Black, Hispanic/Latino, Asian, Indigenous, Other 
+* **Education Level**: No high school, High school graduate, College graduate, Post-graduate 
+* **Income Bracket**: <$30,000, \$30,000-\$60,000, \$60,000-\$100,000, >\$100,000 
+* **Geographic Region**: Northeast, Midwest, South, West
+
+## Budget Allocation
+* **Marketing and Outreach (Ads and Incentives)**: \$50,000
+
+* **Survey Design and Data Validation**:
+  - Questionnaire Development: \$5,000
+  - Pilot Testing (survey run on small group of people): \$5,000
+  - Google Forms (with built-in validation rules): \$5,000
+
+* **Data Analysis and Software**: 
+  - Statistical Software: \$5,000
+  - Staff Fees (Analysts and Statisticians): \$15,000
+
+* **Financial Incentives**: \$2,000
+* **Miscellaneous Expenses and Contingency Fund**: \$8,000
+
+###  **Survey Structure**:
 The survey will begin by introducing each potential participant to the topic and providing necessary context about the purpose of the research.

### 2024-10-30 scripts/cleaning.R
Updating the cleaned data and the model

@@ -26,12 +26,10 @@ analysis_data <- raw_data |>
                                                           "Nevada", "North Carolina", 
                                                           "Pennsylvania", "Wisconsin"), 1, 0)) |>
                  filter(start_date >= as.Date("2024-07-21"),
-                        party %in% c("DEM", "REP"), 
-                        numeric_grade >= 2.6,
-                        swing_state == 1) |>
+                        party %in% c("DEM", "REP")) |>
                  select(poll_id, pollster, numeric_grade, state,start_date, 
                         end_date, sample_size, population, election_date, party, 
-                        answer, candidate_name, pct, candidate_trump) |>
+                        answer, candidate_name, pct, candidate_trump, swing_state) |>
                  drop_na()
 
 #### Save data as parquet file ####

### 2024-10-30 scripts/modeling.R

@@ -18,6 +18,7 @@ library(rstanarm)
 library(arrow)
 library(caret)
 library(MLmetrics)
+library(modelsummary)
 
 model_data <- read_parquet("data/analysis_data/analysis_data.parquet")
 
@@ -33,12 +34,12 @@ set.seed(12)
 training_index <- createDataPartition(model_data$state, p = 0.7, list = FALSE)
 
 training_data <- model_data[training_index,]
-testing_data <- model_data[-training_index,]
+testing_data <- model_data[-training_index,] |> filter(swing_state == 1)
 
 testing_data <- testing_data |> filter(pollster %in% unique(training_data$pollster))
 
 priors <- normal(0.5, 2.5, autoscale = TRUE)
-formula <- candidate_trump ~ (1 | pollster) + (1 | state) + sample_size + pct + days_to_election
+formula <- candidate_trump ~ (1 | pollster) + (1 | state) + pct
 
 model <- stan_glmer(
   formula = formula,
@@ -72,10 +73,10 @@ predicted_data |>
 
 F1_Score(predicted_data$candidate_trump, predicted_data$winner_trump)
 
-RMSE(predicted_data$pct, predicted_data$predicted_pct)
+RMSE(predicted_data$candidate_trump, predicted_data$predicted_pct/100)
 
 #### Save model ####
 saveRDS(
-  election_model,
+  model,
   file = "models/election_model.rds"
 )

### 2024-10-30 paper/paper.qmd
Adding the results table to the paper

@@
 [WORDS]
+
+```{r, echo = FALSE, message = FALSE, warning = FALSE}
+library(tidyverse)
+library(rstanarm)
+library(caret)
+library(kableExtra)
+library(arrow)
+
+electoral_votes <- data.frame(
+  state = c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", 
+            "Connecticut", "Delaware", "District of Columbia", "Florida", "Georgia", 
+            "Hawaii", "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky", 
+            "Louisiana", "Maine", "Maryland", "Massachusetts", "Michigan", "Minnesota",
+            "Mississippi", "Missouri", "Montana", "Nebraska", "Nevada", 
+            "New Hampshire", "New Jersey", "New Mexico", "New York", "North Carolina", 
+            "North Dakota", "Ohio", "Oklahoma", "Oregon", "Pennsylvania", 
+            "Rhode Island", "South Carolina", "South Dakota", "Tennessee", "Texas", 
+            "Utah", "Vermont", "Virginia", "Washington", "West Virginia", "Wisconsin", 
+            "Wyoming"),
+  votes = c(9, 3, 11, 6, 54, 10, 7, 3, 3, 30, 16, 4, 4, 19, 11, 6, 6, 8, 8, 4, 10, 11, 
+            15, 10, 6, 10, 4, 5, 6, 4, 14, 5, 28, 16, 3, 17, 7, 8, 19, 4, 9, 3, 11, 
+            40, 6, 3, 13, 12, 4, 10, 3)
+)
+
+set.seed(12)
+data <- read_parquet("../data/analysis_data/analysis_data.parquet")
+model <- readRDS("../models/election_model.rds")
+training_index <- createDataPartition(data$candidate_trump, p = 0.7, list = FALSE)
+testing_data <- data[-training_index,]
+
+testing_data |>
+  select(pollster, state, candidate_trump, pct) |>
+  mutate(
+    state = recode(state, "Maine CD-1" = "Maine", 
+                          "Maine CD-2" = "Maine",
+                          "Nebraska CD-2" = "Nebraska"),
+    predicted_pct = 100 * posterior_predict(model, newdata = testing_data, 
+                                                  draws = 2000, type = "response") |> colMeans(),
+    winner_trump = ifelse(predicted_pct > 50, 1, 0)
+  ) |>
+  group_by(state) |> 
+  summarise(predicted_prob = round(mean(predicted_pct), 2), .groups = "drop") |>
+  left_join(electoral_votes, by = c("state" = "state")) |>
+  mutate(predicted_winner = ifelse(predicted_prob > 50, "Trump", "Harris")) |>
+  kbl(booktabs = TRUE, col.names = c("State", "Predicted Trump %", "Electoral Votes", "Predicted Winner"))
+```
 

### 2024-10-31 scripts/simulation.R
Updating the simulated data and its tests

@@ -1,7 +1,7 @@
 #### Preamble ####
-# Purpose: Simulates a mock dataset of surveyed individuals.
-# Author: Sameeck Bhatia
-# Date: 14 October 2024
+# Purpose: Simulates a mock dataset of polls in each state.
+# Author: Sameeck Bhatia, Sean Chua, Tanmay Shinde
+# Date: 30 October 2024
 # Contact: sameeck.bhatia@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
@@ -15,25 +15,44 @@ set.seed(12)
 
 
 #### Simulate data ####
-states <- c("AL", "AK", "AR", "AZ", "CA")
-num_districts <- setNames(c(7, 1, 9, 4, 52), states)
-races <- c("w", "b", "h", "a", "n", "o")
-parties <- c("d", "r", "i")
-voter_types <- c("registered", "likely")
+pollsters <- c("Emerson", "Morning Consult", "Siena/NYT", "YouGov")
+states <- c("AZ", "FL", "GA", "NY", "WA")
+populations <- c("likely", "registered")
+dates <- seq(from = as.Date("2024-07-21"), to = as.Date("2024-10-30"), by = 1)
 
-n <- 1000
+n <- 50
 
-simulated_data <- data.frame(
-  "id" = sample(10000:99999, n, replace = FALSE),
-  "state" = sample(states, n, replace = TRUE),
-  "race" = sample(races, n, replace = TRUE, prob = c(60, 13, 19, 6, 1, 1)),
-  "party" = sample(parties, n, replace = TRUE, prob = c(51, 47, 2)),
-  "last_election" = sample(parties, n, replace = TRUE, prob = c(48, 46, 6)),
-  "voter_type" = sample(voter_types, n, replace = TRUE, prob = c(66, 34))
-)
+simulated_data1 <- data.frame(
+  "poll_id" = sample(10000:49999, n, replace = FALSE),
+  "pollster" = sample(pollsters, n, replace = TRUE, prob = c(124, 272, 180, 30)),
+  "state" = sample(states, n, replace = TRUE, prob = c(2, 6, 3, 6, 2)),
+  "sample_size" = rpois(n, 800),
+  "population" = sample(populations, n, replace = TRUE, prob = c(66, 34)),
+  "end_date" = sample(dates, n, replace = TRUE),
+  "candidate" = "Trump"
+  ) |>
[…]

### 2024-10-31 scripts/test_simulation.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Tests whether the simulated data is valid and is the required size.
-# Author: Sameeck Bhatia
-# Date: 14 October 2024
+# Author: Sameeck Bhatia, Sean Chua, Tanmay Shinde
+# Date: 30 October 2024
 # Contact: sameeck.bhatia@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
@@ -26,22 +26,53 @@ if (exists("simulated_data")) {
 
 
 #### Test data ####
-test_that("The dataset has 1000 observations", {
-  expect_equal(nrow(simulated_data), 1000)
+test_that("poll_id values are unique", {
+  expect_equal(any(duplicated(simulated_data$poll_id)), FALSE)
 })
 
-test_that("Each state has at least 1 congressional district and at most 52", {
-  expect_in(range(simulated_data$district), c(1, 52))
+test_that("State, population, and candidate contain expected values only", {
+  expected_states <- c("AZ", "FL", "GA", "NY", "WA")
+  expected_populations <- c("likely", "registered")
+  expected_candidates <- c("Trump", "Harris")
+  
+  expect_true(all(simulated_data$state %in% expected_states))
+  expect_true(all(simulated_data$population %in% expected_populations))
+  expect_true(all(simulated_data$candidate %in% expected_candidates))
 })
 
-test_that("There are three parties in the dataset", {
-  expect_length(unique(simulated_data$party), 3)
+test_that("end_date is within the expected date range", {
+  expect_true(all(simulated_data$end_date >= as.Date("2024-07-21")))
+  expect_true(all(simulated_data$end_date <= as.Date("2024-10-30")))
 })
 
-test_that("All surveyor IDs are unique", {
-  expect_length(unique(simulated_data$id), 1000)
+test_that("sample_size is within a reasonable range", {
+  expect_true(all(simulated_data$sample_size > 100))
+  expect_true(all(simulated_data$sample_size < 2000))
 })
 
-test_that("At least one reponse of each race is in the dataset", {
-  expect_contains(unique(simulated_data$race), c("w", "b", "h", "a", "n", "o"))
+test_that("percent is within the range 0-100", {
+  expect_true(all(simulated_data$percent >= 0 & simulated_data$percent <= 100))
+})
+
+test_that("mean percent aligns with state-specific expectations", {
[…]

### 2024-11-01 scripts/cleaning.R
Updating the analysis data folder

@@ -18,19 +18,14 @@ library(arrow)
 raw_data <- read_csv("data/raw_data/raw_data.csv")
 
 analysis_data <- raw_data |>
-                 mutate(start_date = mdy(start_date),
-                        end_date = mdy(end_date),
-                        election_date = mdy(election_date),
-                        candidate_trump = ifelse(candidate_name == "Donald Trump", 1, 0),
-                        swing_state = ifelse(state %in% c("Arizona", "Georgia", "Michigan", 
-                                                          "Nevada", "North Carolina", 
-                                                          "Pennsylvania", "Wisconsin"), 1, 0)) |>
-                 filter(start_date >= as.Date("2024-07-21"),
-                        party %in% c("DEM", "REP")) |>
-                 select(poll_id, pollster, numeric_grade, state,start_date, 
-                        end_date, sample_size, population, election_date, party, 
-                        answer, candidate_name, pct, candidate_trump, swing_state) |>
-                 drop_na()
+  mutate(start_date = mdy(start_date),
+         end_date = mdy(end_date),
+         election_date = mdy(election_date)) |>
+  filter(start_date >= as.Date("2024-07-21")) |>
+  select(poll_id, pollster, numeric_grade, state,start_date, 
+        end_date, sample_size, population, election_date, party, 
+        answer, candidate_name, pct) |>
+  drop_na()
 
 #### Save data as parquet file ####
 write_parquet(x = analysis_data, sink = "data/analysis_data/analysis_data.parquet")

### 2024-11-01 scripts/modeling.R
Creating per-candidate models

@@ -26,6 +26,11 @@ model_data <- model_data |>
   mutate(pollster = as.factor(pollster),
          state = as.factor(state),
          population = as.factor(population),
+         candidate_trump = ifelse(answer == "Trump", 1, 0),
+         candidate_harris = ifelse(answer == "Harris", 1, 0),
+         swing_state = ifelse(state %in% c("Arizona", "Georgia", "Michigan",
+                                           "Nevada", "North Carolina", "Pennsylvania",
+                                           "Wisconsin"), 1, 0),
          weight = numeric_grade * (sample_size / min(sample_size)),
          days_to_election = as.numeric(election_date - end_date))
 
@@ -34,15 +39,17 @@ set.seed(12)
 training_index <- createDataPartition(model_data$state, p = 0.7, list = FALSE)
 
 training_data <- model_data[training_index,]
-testing_data <- model_data[-training_index,] |> filter(swing_state == 1)
+testing_data <- model_data[-training_index,]
 
 testing_data <- testing_data |> filter(pollster %in% unique(training_data$pollster))
 
-priors <- normal(0.5, 2.5, autoscale = TRUE)
-formula <- candidate_trump ~ (1 | pollster) + (1 | state) + pct
+write_parquet(training_data, sink = "data/analysis_data/training_data.parquet")
+write_parquet(testing_data, sink = "data/analysis_data/testing_data.parquet")
 
-model <- stan_glmer(
-  formula = formula,
+priors <- normal(0.5, 2, autoscale = TRUE)
+
+trump_model <- stan_glmer(
+  formula = candidate_trump ~ (1 | pollster) + (1 | state) + pct,
   data = training_data,
   family = binomial(link = "logit"),
   prior = priors,
@@ -54,29 +61,50 @@ model <- stan_glmer(
   seed = 12
 )
 
-pp_check(model)
+harris_model <- stan_glmer(
+  formula = candidate_harris ~ (1 | pollster) + (1 | state) + pct,
+  data = training_data,
+  family = binomial(link = "logit"),
+  prior = priors,
+  prior_intercept = priors,
+  weights = weight,
+  cores = 4,
+  iter = 2000,
+  adapt_delta = 0.95,
+  seed = 12
+)
+
+pp_check(trump_model)
+pp_check(harris_model)
 
 set.seed(12)
 
-predicted_data <- testing_data |>
-  select(pollster, state, candidate_trump, pct) |>
[…]

### 2024-11-01 scripts/modeling.R
Updating the model and analysis data folder

@@ -16,7 +16,7 @@
 library(tidyverse)
 library(rstanarm)
 library(arrow)
-library(caret)
+library(rsample)
 library(MLmetrics)
 library(modelsummary)
 
@@ -36,17 +36,23 @@ model_data <- model_data |>
 
 set.seed(12)
 
-training_index <- createDataPartition(model_data$state, p = 0.7, list = FALSE)
+model_data$state_answer <- interaction(model_data$state, model_data$answer, drop = TRUE)
 
-training_data <- model_data[training_index,]
-testing_data <- model_data[-training_index,]
+split <- initial_split(model_data, prop = 0.7, strata = state_answer)
 
-testing_data <- testing_data |> filter(pollster %in% unique(training_data$pollster))
+training_data <- training(split)
+testing_data <- testing(split)
+
+testing_data <- testing_data |> 
+  filter(pollster %in% unique(training_data$pollster)) |> 
+  select(!state_answer)
+
+testing_data |> filter(answer == "Harris") |> group_by(state) |> summarise(mean_pct = mean(pct))
 
 write_parquet(training_data, sink = "data/analysis_data/training_data.parquet")
 write_parquet(testing_data, sink = "data/analysis_data/testing_data.parquet")
 
-priors <- normal(0.5, 2, autoscale = TRUE)
+priors <- normal(0.5, 3, autoscale = TRUE)
 
 trump_model <- stan_glmer(
   formula = candidate_trump ~ (1 | pollster) + (1 | state) + pct,
@@ -81,13 +87,17 @@ set.seed(12)
 
 predicted_data_trump <- testing_data |>
   select(pollster, state, swing_state, candidate_trump, pct) |>
-  mutate(predicted_pct =  100 * posterior_predict(trump_model, newdata = testing_data, type = "response") |> colMeans(),
-         winner_trump = ifelse(predicted_pct > 50, 1, 0))
+  mutate(predicted_pct_trump =  100 * posterior_predict(trump_model, newdata = testing_data, type = "response") |> colMeans(),
+         winner_trump = ifelse(predicted_pct_trump > 50, 1, 0))
 
 predicted_data_harris <- testing_data |>
   select(pollster, state, swing_state, candidate_harris, pct) |>
-  mutate(predicted_pct =  100 * posterior_predict(harris_model, newdata = testing_data, type = "response") |> colMeans(),
[…]

### 2024-11-01 paper/paper.qmd
Updating the table in the paper

@@
 
-set.seed(12)
-data <- read_parquet("../data/analysis_data/analysis_data.parquet")
-model <- readRDS("../models/election_model.rds")
-training_index <- createDataPartition(data$candidate_trump, p = 0.7, list = FALSE)
-testing_data <- data[-training_index,]
+predicted_data <- read_parquet("../data/analysis_data/predicted_data.parquet")
 
-testing_data |>
-  select(pollster, state, candidate_trump, pct) |>
-  mutate(
-    state = recode(state, "Maine CD-1" = "Maine", 
-                          "Maine CD-2" = "Maine",
-                          "Nebraska CD-2" = "Nebraska"),
-    predicted_pct = 100 * posterior_predict(model, newdata = testing_data, 
-                                                  draws = 2000, type = "response") |> colMeans(),
-    winner_trump = ifelse(predicted_pct > 50, 1, 0)
-  ) |>
+predicted_data_trump <- predicted_data |>
+  filter(candidate_trump == 1) |>
+  select(state, pct, predicted_pct_trump) |>
+  mutate(state = recode(state, "Maine CD-1" = "Maine", "Maine CD-2" = "Maine",
+                        "Nebraska CD-2" = "Nebraska")) |>
   group_by(state) |>
-  summarise(predicted_prob = round(mean(predicted_pct), 2), .groups = "drop") |>
+  summarise(predicted_pct_trump = round(mean(predicted_pct_trump), 2))
+
+predicted_data_harris <- predicted_data |>
+  filter(candidate_harris == 1) |>
+  select(state, pct, predicted_pct_harris) |>
+  mutate(state = recode(state, "Maine CD-1" = "Maine", "Maine CD-2" = "Maine",
+                        "Nebraska CD-2" = "Nebraska")) |>
+  group_by(state) |>
+  summarise(predicted_pct_harris = round(mean(predicted_pct_harris), 2))
+
+predicted_data_harris |> 
+  merge(predicted_data_trump, all = T) |>
   left_join(electoral_votes, by = c("state" = "state")) |>
-  mutate(predicted_winner = ifelse(predicted_prob > 50, "Trump", "Harris")) |>
-  kbl(booktabs = TRUE, col.names = c("State", "Predicted Trump %", "Electoral Votes", "Predicted Winner"))
+  mutate(predicted_winner = ifelse(replace_na(predicted_pct_harris, 50) <
+                                     replace_na(predicted_pct_trump, 50), 
+                                   "Trump", "Harris")) |>
+  kbl(booktabs = TRUE, col.names = c("State", "Predicted Harris %", "Predicted Trump %", "Electoral Votes", "Predicted Winner"))
 ```

### 2024-11-01 scripts/modeling.R
Updating the analysis data folder and model

@@ -47,12 +47,10 @@ testing_data <- testing_data |>
   filter(pollster %in% unique(training_data$pollster)) |> 
   select(!state_answer)
 
-testing_data |> filter(answer == "Harris") |> group_by(state) |> summarise(mean_pct = mean(pct))
-
 write_parquet(training_data, sink = "data/analysis_data/training_data.parquet")
 write_parquet(testing_data, sink = "data/analysis_data/testing_data.parquet")
 
-priors <- normal(0.5, 3, autoscale = TRUE)
+priors <- normal(0.5, 0.25, autoscale = TRUE)
 
 trump_model <- stan_glmer(
   formula = candidate_trump ~ (1 | pollster) + (1 | state) + pct,

### 2024-11-01 paper/paper.qmd
Updating all scripts and data

@@
 # Results {#sec-results}
-[WORDS]
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Ut elit leo, viverra ac enim non, pulvinar aliquam nisl.
+Nam accumsan ac nisi at consectetur.
+Curabitur luctus lacus eget risus rutrum, vel facilisis urna feugiat.
+Ut ac dictum velit, in blandit augue.
+Fusce sit amet vehicula dui.
+Suspendisse eleifend tempor rhoncus.
+Cras vehicula, nisl et molestie pulvinar, lorem ex dictum augue, nec mollis leo sem quis mauris.
+In lacus massa, maximus vel vehicula in, tincidunt sed lorem.
+Proin commodo pulvinar dictum.
+Vestibulum eleifend, metus ac luctus molestie, velit odio cursus nisl, sed lobortis arcu massa id diam.
+Curabitur convallis erat a ultricies dictum.
+In imperdiet ultricies nibh, quis condimentum nulla mattis non.
+
+Aliquam erat volutpat.
+Praesent in erat sit amet purus auctor posuere ut vitae leo.
+Suspendisse potenti.
+Interdum et malesuada fames ac ante ipsum primis in faucibus.
+Ut blandit vel orci vel aliquam.
+Curabitur a turpis vestibulum enim interdum consectetur at et dui.
+Praesent ut mauris maximus, auctor nisl ac, eleifend sapien.
+Morbi non varius urna.
+Ut placerat vestibulum nisi in lacinia.
+Aliquam non ultrices arcu, et rhoncus dolor.
+Suspendisse vel pulvinar tortor.
+Nulla lacinia sapien sollicitudin, vestibulum nulla id, hendrerit nisl.
+
+Quisque pulvinar, enim a volutpat scelerisque, odio arcu condimentum velit, convallis vehicula velit augue id odio.
+Aenean ligula augue, mollis sit amet mi eu, ullamcorper aliquam massa.
+Aenean rutrum diam purus, eu porta mi blandit vitae.
+Phasellus luctus eleifend orci, nec aliquet mauris eleifend id.
+Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
+Sed elementum, magna sed finibus tincidunt, turpis orci viverra ligula, in sollicitudin nunc ex sed orci.
+Curabitur et purus tortor.
+Maecenas volutpat enim nisi, in ornare lectus venenatis id.
+In non enim dui.
+Suspendisse id eros in nisi consequat aliquet vel sed mi.
+Aenean placerat elementum semper.
 
@@
   mutate(state = recode(state, "Maine CD-1" = "Maine", "Maine CD-2" = "Maine",
-                        "Nebraska CD-2" = "Nebraska")) |>
+                        "Nebraska CD-2" = "Nebraska", "Nebraska CD-3" = "Nebraska")) |>
   group_by(state) |>
@@
 ```
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Ut elit leo, viverra ac enim non, pulvinar aliquam nisl.
+Nam accumsan ac nisi at consectetur.
+Curabitur luctus lacus eget risus rutrum, vel facilisis urna feugiat.
+Ut ac dictum velit, in blandit augue.
+Fusce sit amet vehicula dui.
+Suspendisse eleifend tempor rhoncus.
+Cras vehicula, nisl et molestie pulvinar, lorem ex dictum augue, nec mollis leo sem quis mauris.
+In lacus massa, maximus vel vehicula in, tincidunt sed lorem.
+Proin commodo pulvinar dictum.
+
+Aliquam erat volutpat.
+Praesent in erat sit amet purus auctor posuere ut vitae leo.
+Suspendisse potenti.
+Interdum et malesuada fames ac ante ipsum primis in faucibus.
+Ut blandit vel orci vel aliquam.
+Curabitur a turpis vestibulum enim interdum consectetur at et dui.
+Praesent ut mauris maximus, auctor nisl ac, eleifend sapien.
+Morbi non varius urna.
+Ut placerat vestibulum nisi in lacinia.
+
+Quisque pulvinar, enim a volutpat scelerisque, odio arcu condimentum velit, convallis vehicula velit augue id odio.
+Aenean ligula augue, mollis sit amet mi eu, ullamcorper aliquam massa.
+Aenean rutrum diam purus, eu porta mi blandit vitae.
+Phasellus luctus eleifend orci, nec aliquet mauris eleifend id.
+Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
+
+```{r, fig.width = 8, fig.height=6, echo = FALSE, message = FALSE}
+predicted_data |>
+  filter(swing_state == 1, candidate_trump == 1) |>
+  select(state, end_date, predicted_pct_trump) |>
+  group_by(state, end_date) |>
+  summarise(mean = mean(predicted_pct_trump), .groups = "drop") |>
+  ggplot(aes(x = end_date, y = mean)) +
+  geom_point(size = 0.5) +
+  scale_y_continuous(limits = c(0, 100)) +
+  geom_smooth(se = FALSE, color = "red2", method = "loess", formula = 'y ~ x') +
+  facet_wrap(vars(state)) +
+  labs(x = NULL, y = NULL)
+```
+
+```{r, warning = FALSE, echo = FALSE, fig.width = 8, fig.height = 6}
+library(ggplot2)
+library(dplyr)
+
+# Prepare combined data for both candidates
+combined_data <- predicted_data |>
+  filter(candidate_trump == 1 | candidate_harris == 1) |>
+  select(state, end_date, pct, candidate_trump, candidate_harris) |>
+  group_by(state, end_date) |>
+  summarise(
+    mean_trump = mean(pct[candidate_trump == 1]),
+    mean_harris = mean(pct[candidate_harris == 1]),
+    .groups = "drop"
+  )
+
+# Melt the data for easier plotting
+combined_data_long <- combined_data |>
+  pivot_longer(cols = c(mean_trump, mean_harris),
+               names_to = "candidate",
+               values_to = "mean")
+
+# Create the overlay plot
+overlay_plot <- ggplot(combined_data_long, aes(x = end_date, y = mean, color = candidate)) +
+  geom_point(size = 0.5) +
+  geom_smooth(se = FALSE, method = "loess", formula = 'y ~ x') +
+  scale_y_continuous(limits = c(0, 100)) +
+  labs(x = NULL, y = NULL, color = "Candidate") +
+  scale_color_manual(values = c("mean_trump" = "red2", "mean_harris" = "blue2")) +
+  theme(legend.position = "top")
+
+# Display the overlay plot
+print(overlay_plot)
+```
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Ut elit leo, viverra ac enim non, pulvinar aliquam nisl.
+Nam accumsan ac nisi at consectetur.
+Curabitur luctus lacus eget risus rutrum, vel facilisis urna feugiat.
+Ut ac dictum velit, in blandit augue.
+Fusce sit amet vehicula dui.
+Suspendisse eleifend tempor rhoncus.
+Cras vehicula, nisl et molestie pulvinar, lorem ex dictum augue, nec mollis leo sem quis mauris.
+
+Aliquam erat volutpat.
+Praesent in erat sit amet purus auctor posuere ut vitae leo.
+Suspendisse potenti.
+Interdum et malesuada fames ac ante ipsum primis in faucibus.
+Ut blandit vel orci vel aliquam.
+Curabitur a turpis vestibulum enim interdum consectetur at et dui.
+Praesent ut mauris maximus, auctor nisl ac, eleifend sapien.
+Morbi non varius urna.
+Ut placerat vestibulum nisi in lacinia.
+
+Quisque pulvinar, enim a volutpat scelerisque, odio arcu condimentum velit, convallis vehicula velit augue id odio.
+Aenean ligula augue, mollis sit amet mi eu, ullamcorper aliquam massa.
+Aenean rutrum diam purus, eu porta mi blandit vitae.
+Phasellus luctus eleifend orci, nec aliquet mauris eleifend id.
+Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
 

### 2024-11-01 scripts/modeling.R

@@ -84,12 +84,12 @@ pp_check(harris_model)
 set.seed(12)
 
 predicted_data_trump <- testing_data |>
-  select(pollster, state, swing_state, candidate_trump, pct) |>
+  select(pollster, state, start_date, end_date, swing_state, candidate_trump, pct) |>
   mutate(predicted_pct_trump =  100 * posterior_predict(trump_model, newdata = testing_data, type = "response") |> colMeans(),
          winner_trump = ifelse(predicted_pct_trump > 50, 1, 0))
 
 predicted_data_harris <- testing_data |>
-  select(pollster, state, swing_state, candidate_harris, pct) |>
+  select(pollster, state, start_date, end_date, swing_state, candidate_harris, pct) |>
   mutate(predicted_pct_harris =  100 * posterior_predict(harris_model, newdata = testing_data, type = "response") |> colMeans(),
          winner_harris = ifelse(predicted_pct_harris > 50, 1, 0))
 

### 2024-11-01 scripts/test_analysis.R

@@ -14,8 +14,9 @@
 #### Workspace setup ####
 library(tidyverse)
 library(testthat)
+library(arrow)
 
-data <- read_csv("data/analysis_data/analysis_data.csv")
+data <- read_parquet("data/analysis_data/analysis_data.parquet")
 
 # Test if the data was successfully loaded
 if (exists("data")) {

### 2024-11-01 paper/paper.qmd
Updating figures in the paper

@@
   scale_y_continuous(limits = c(0, 100)) +
-  geom_smooth(se = FALSE, color = "red2", method = "loess", formula = 'y ~ x') +
+  geom_smooth(se = FALSE, color = "#d92b34", method = "loess", formula = 'y ~ x') +
   facet_wrap(vars(state)) +
@@
   labs(x = NULL, y = NULL, color = "Candidate") +
-  scale_color_manual(values = c("mean_trump" = "red2", "mean_harris" = "blue2")) +
+  scale_color_manual(values = c("mean_trump" = "#d92b34", "mean_harris" = "#2635bd")) +
   theme(legend.position = "top")
@@
 Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
+
+```{r, echo = FALSE, fig.height=6, fig.width=8, warning = FALSE}
+library(usmap)
+
+sample <- predicted_data_harris |> 
+  merge(predicted_data_trump, all = T) |>
+  left_join(electoral_votes, by = c("state" = "state")) |>
+  mutate(predicted_winner = ifelse(replace_na(predicted_pct_harris, 50) <
+                                     replace_na(predicted_pct_trump, 50), 
+                                   "Trump", "Harris"))
+
+plot_usmap(regions = "state", data = sample, 
+           values = "predicted_winner") +
+  scale_fill_manual(values = c("#2635bd", "#d92b34", "grey90")) +
+  theme(legend.position = "top")
+```
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Ut elit leo, viverra ac enim non, pulvinar aliquam nisl.
+Nam accumsan ac nisi at consectetur.
+Curabitur luctus lacus eget risus rutrum, vel facilisis urna feugiat.
+Ut ac dictum velit, in blandit augue.
+Fusce sit amet vehicula dui.
+Suspendisse eleifend tempor rhoncus.
+Cras vehicula, nisl et molestie pulvinar, lorem ex dictum augue, nec mollis leo sem quis mauris.
+
+Aliquam erat volutpat.
+Praesent in erat sit amet purus auctor posuere ut vitae leo.
+Suspendisse potenti.
+Interdum et malesuada fames ac ante ipsum primis in faucibus.
+Ut blandit vel orci vel aliquam.
+Curabitur a turpis vestibulum enim interdum consectetur at et dui.
+Praesent ut mauris maximus, auctor nisl ac, eleifend sapien.
+Morbi non varius urna.
+Ut placerat vestibulum nisi in lacinia.
 

### 2024-11-01 paper/paper.qmd
Updated paper + added references

@@
 ```{r, echo = FALSE, message = FALSE, warning = FALSE}
+#| label: tbl-prediction
+#| echo: false
+#| 
 library(tidyverse)
@@
 
-## First discussion point {#sec-first-point}
+## Harris Wins the Swing States and Overcomes the Bradley Effect
+Named after Thomas Bradley, a Los Angeles Mayor who underperformed his polls in the 80s, the Bradley Effect is when a candidate does poorly on polls due to his or her gender and/or race [@natesilvergut].
+From the @tbl-prediction, we can see that Harris wins the majority of the seven swing states,states where "both major parties enjoy similar levels of support among the voting population [@citeSwing]." With these states being the most pivotal toward Harris's path to victory, our prediction of Harris overcoming the Bradley effect, in spite of being a Black woman, bodes well for her in the upcoming election.
+It is important to realize that due to the nature of the Electoral College, it is possible to not win the popular vote but win the election, and these swing states play a major factor in this regard.
+Real-world polls, however, show Trump narrowly winning four out of seven swing states (however, the predicted margin of victory still lies within standard error margins of these polls).
+```{r, echo = FALSE, message = FALSE, warning = FALSE}
+library(dplyr)
+library(knitr)
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
-Mauris non libero vel ligula tincidunt consequat.
-Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
-Vivamus feugiat et quam ut consequat.
-Aenean mollis ullamcorper facilisis.
-Vivamus scelerisque lectus et elementum vulputate.
-Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
-Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
-Curabitur vitae tortor nec ligula scelerisque rutrum.
-Nullam feugiat odio metus.
-Cras id convallis ante, ut ornare velit.
-Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
+swing_states_data <- data.frame(
+  State = c("Pennsylvania", "North Carolina", "Michigan", "Wisconsin", "Georgia", "Arizona", "Nevada"),
+  Poll_1 = c(47.7, 47.5, 48.4, 48.5, 47.4, 46.8, 48.0),
+  Poll_2 = c(47.7, 47.5, 48.4, 48.5, 47.4, 46.8, 48.0),
+  Poll_3 = c(48.3, 48.6, 47.2, 47.8, 49.2, 48.9, 47.9),
+  Poll_4 = c(48.3, 48.6, 47.2, 47.8, 49.2, 48.9, 47.9),
+  Margin = c("R+ 0.6", "R+ 1.1", "D+ 1.2", "D+ 0.7", "R+ 1.8", "R+ 2.1", "D+ 0.1")
+)
 
-## Second discussion point
+kable(swing_states_data, caption = "Swing States Polling Data as of October 31, 2024")
+```
+It is important to note that the margin of victories in each swing state are within the 2 to 5% margin of error of most polls; it cannot be said for certain who wins these states until Election Day.
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
-Mauris non libero vel ligula tincidunt consequat.
-Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
-Vivamus feugiat et quam ut consequat.
-Aenean mollis ullamcorper facilisis.
-Vivamus scelerisque lectus et elementum vulputate.
-Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
-Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
-Curabitur vitae tortor nec ligula scelerisque rutrum.
-Nullam feugiat odio metus.
-Cras id convallis ante, ut ornare velit.
-Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
+## More Urban States Tend to Lean Harris
 
-## Third discussion point
+From our results in @tbl-prediction, we see that Harris has significant leads in states like California and Maryland; from @tbl-urban, notice that these states have a relatively high level of urban population, with 94.2% and 85.6% respectively.
+One reason for this could be attributed to the higher proportion of educated people in urban areas as opposed to rural ones.
+This allows people to gain more knowledge in diverse topics such as politics and climate change [@thisnation] and adopt a progressive mindset, which is in line with the ideals of the Democratic Party.
+In this regard, heavily urban-populated areas tend to be more culturally diverse and open to liberal ideas [@washu_urban_rural].
+Moreover, the article states that "people living in rural areas tend to have traditional values and be resistant to new ideas" which goes against the progressive mindset imbibed by Democrats.
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
-Mauris non libero vel ligula tincidunt consequat.
-Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
-Vivamus feugiat et quam ut consequat.
-Aenean mollis ullamcorper facilisis.
-Vivamus scelerisque lectus et elementum vulputate.
-Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
-Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
-Curabitur vitae tortor nec ligula scelerisque rutrum.
-Nullam feugiat odio metus.
-Cras id convallis ante, ut ornare velit.
-Mauris turpis purus, porttitor eu leo quis, suscipit euismod ligula.
-
-## Weaknesses and next steps
+## Limitations and Areas for Future Research
 
@@
 # Additional Data Details
+```{r}
+#| label: tbl-urban
+#| echo: false
+states_data <- data.frame(
+  state = c("Alabama", "Alaska", "Arizona", "Arkansas", "California", 
+            "Colorado", "Connecticut", "Delaware", "Florida", 
+            "Georgia", "Hawaii", "Idaho", "Illinois", "Indiana", 
+            "Iowa", "Kansas", "Kentucky", "Louisiana", "Maine", 
+            "Maryland", "Massachusetts", "Michigan", "Minnesota", 
+            "Mississippi", "Missouri", "Montana", "Nebraska", 
+            "Nevada", "New Hampshire", "New Jersey", "New Mexico",
+            "New York", "North Carolina", "North Dakota",
+            "Ohio", "Oklahoma", "Oregon", "Pennsylvania",
+            "Rhode Island", "South Carolina", "South Dakota",
+            "Tennessee", "Texas", "Utah", "Vermont",
+            "Virginia", "Washington",  "West Virginia",
+            "Wisconsin","Wyoming"),
+  urban_percent_2020 = c(57.7, 64.9, 89.3, 55.5, 94.2,
+                       86.0, 86.3, 82.6, 91.5,
+                       74.1, 86.1, 69.2, 86.9, 71.2,
+                       63.2, 72.3, 58.7, 71.5, 38.6,
+                       85.6, 91.3, 73.5, 71.9, 46.3,
+                       69.5, 53.4, 73.0, 94.1, 58.3,
+                       93.8, 74.5, 87.4, 66.7, 61.0,
+                       76.3, 64.6, 80.5, 76.5, 91.1, 67.9, 57.2, 66.2, 83.7, 89.8, 35.1,
+                       75.6, 83.4, 44.6,
+                       67.1,62)
+)
+kable(states_data, caption = "2020 Percentage of Urban Population for each US State")
+```
 

### 2024-11-02 paper/paper.qmd
Updating the model section in the paper

@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Aliquam auctor quam et justo efficitur, sit amet eleifend elit euismod.
-Mauris non libero vel ligula tincidunt consequat.
-Aenean gravida, risus id auctor aliquam, orci leo auctor tellus, non tincidunt est arcu at lectus.
-Vivamus feugiat et quam ut consequat.
-Aenean mollis ullamcorper facilisis.
-Vivamus scelerisque lectus et elementum vulputate.
-Nulla et arcu vehicula, iaculis felis sit amet, semper justo.
-Suspendisse quam augue, hendrerit a tortor non, tristique feugiat sem.
-Curabitur vitae tortor nec ligula scelerisque rutrum.
+## Overview
 
-## Model set-up
-A Bayesian approach is used in constructing our model. As such, an informative prior is assumed, and logistic regression is implemented due to the nature of the outcome variable (binary).
+This section describes a predictive Bayesian model for estimating voter support for two candidates—Donald Trump and Kamala Harris—in the 2024 U.S.
+presidential election.
+The model separately estimates the proportion of support for each candidate in 37 states, including both swing states (e.g., Georgia, Arizona) and strongholds (e.g., California, Texas).
+The “Trump” model and “Harris” model each output the probability that a voter supports Trump or Harris, respectively, based on pollster reliability, state, and polling percentages.
 
-The predictor variables used in the model are as follows:
+## Model Structure
 
-- **Sample Size (`sample_size`)**: The number of respondents in the poll.
-- **State (`state`)**: A categorical variable for different U.S. states.
-- **Days to Election (`days_to_election`)**: Counts the number of days until Election Day starting from today’s date (it also uses `end_date` from the original dataset).
-- **Voter Percentage of Candidate (`pct`)**: A continuous variable for the percentage of voters who plan to vote for Trump based on polling data.
+The Trump and Harris models share a similar structure, represented by the following equations:
 
-The model takes the form of the following equation [TO-DO]:
+- **Trump Model**:
 \begin{align}
-\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{transparency\_score}_i \\
-             &\quad + \beta_3 \cdot \text{sample\_size}_i + \beta_4 \cdot \text{state}_i + \beta_5 \cdot \text{end\_date}_i + \epsilon_i \\
-\epsilon_i &\sim \text{Normal}(0, \sigma^2)
+\text{predicted\_pct\_trump} = \beta_0 + \beta_1 \cdot (1 | \text{pollster}) + \beta_2 \cdot (1 | \text{state}) + \beta_3 \cdot \text{pct}
 \end{align}
 
-Where: 
+- **Harris Model**:
 \begin{align}
-\beta_0 & \text{ is the intercept term} \\
-\beta_1, \beta_2, \beta_3, \beta_4, \beta_5 & \text{ are the coefficients for each predictor} \\
-\sigma^2 & \text{ is the variance of the error term}
+\text{predicted\_pct\_harris} = \beta_0 + \beta_1 \cdot (1 | \text{pollster}) + \beta_2 \cdot (1 | \text{state}) + \beta_3 \cdot \text{pct}
 \end{align}
 
+Here, $\beta_0$, $\beta_1$, $\beta_2$, and $\beta_3$ are the model coefficients.
+Here $\beta_0$ is the intercept or the baseline percentage, and $\beta_1$, $\beta_2$ are the mean percentage point change in the predicted percentage, while $\beta_3$ is the mean change in the response for a one percentage point change in the polling percentage.
+For each model, the indicator variable (1 if the candidate is Trump for the "Trump" model and Harris for the "Harris" model, 0 otherwise) represents the response, with pollster, state, and polling percentage as predictors.
+Random effects for "pollster" account for polling agency bias, and random effects for "state" capture state-level variations in voter support.
+
+## Predictors and Weights
+
+- **Pollster:** Different polling agencies show varying levels of reliability. We assign weights to pollsters based on their sample sizes and a numeric grade (0 to 3, with 3 being the most reliable).
+- **State:** By including states as a predictor, the model considers unique voter patterns by location, essential for identifying swing states and strongholds.
+- **Polling Percentage (pct):** The polling percentage represents the actual polling data, which directly informs our estimate of voter support for each candidate.
+
+## Priors
+
+For this Bayesian model, we use a normal prior with a mean of 0.5 (50%) and a standard deviation of 0.25 (25%).
+This prior assumes a close race between Trump and Harris, allowing for a reasonable degree of uncertainty without overconfidence in either direction.
+These parameters reflect the consensus of a competitive 2024 election.
+
+## Assumptions and Limitations
+
+The model assumes additional candidates besides Trump and Harris, addressed by separate models for each candidate.
+However, this dual-model approach may introduce error by not considering third-party effects directly.
+Furthermore, the model is limited to the 37 states included and cannot generalize predictions for other states (e.g., Idaho, Vermont).
+
+## Software Implementation
+
+The model was developed in R using the rstanarm package for Bayesian modeling, including priors, posteriors, and predictions.
+
+## Model Validation
+
+Model validation and performance metrics (F1 Score ~ 0.74, RMSE ~ 0.4) are available in `scripts/modeling.R`.
+A 70/30 train-test split was applied, with testing conducted exclusively on out-of-sample data.
+These scores indicate a reasonable balance of precision and recall, appropriate for the model’s simplicity and data limitations.
+
+## Alternative Models
+
+Alternative models considered included a single binary model (Trump vs.
+Harris) and a version with additional pollscore bias adjustment.
+While these models offer unique insights, they either oversimplify the election’s dynamics or risk overfitting.
+The final model balances simplicity with predictive accuracy.
+
+<!-- A Bayesian approach is used in constructing our model. As such, an informative prior is assumed, and logistic regression is implemented due to the nature of the outcome variable (binary). -->
+
+<!-- The predictor variables used in the model are as follows: -->
+
+<!-- - **Sample Size (`sample_size`)**: The number of respondents in the poll. -->
+<!-- - **State (`state`)**: A categorical variable for different U.S. states. -->
+<!-- - **Days to Election (`days_to_election`)**: Counts the number of days until Election Day starting from today’s date (it also uses `end_date` from the original dataset). -->
+<!-- - **Voter Percentage of Candidate (`pct`)**: A continuous variable for the percentage of voters who plan to vote for Trump based on polling data. -->
+
+<!-- The model takes the form of the following equation [TO-DO]: -->
+<!-- \begin{align} -->
+<!-- \text{pct}_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{transparency\_score}_i \\ -->
+<!--              &\quad + \beta_3 \cdot \text{sample\_size}_i + \beta_4 \cdot \text{state}_i + \beta_5 \cdot \text{end\_date}_i + \epsilon_i \\ -->
+<!-- \epsilon_i &\sim \text{Normal}(0, \sigma^2) -->
+<!-- \end{align} -->
+
+<!-- Where: -->
+<!-- \begin{align} -->
+<!-- \beta_0 & \text{ is the intercept term} \\ -->
+<!-- \beta_1, \beta_2, \beta_3, \beta_4, \beta_5 & \text{ are the coefficients for each predictor} \\ -->
+<!-- \sigma^2 & \text{ is the variance of the error term} -->
+<!-- \end{align} -->
+
 ## Interpretation
-[WORDS TO-DO]
 
-## Model Justification and Evaluation
-[tbl-summary] shows the summary table for the model. 
-F1-Score blabla
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Ut elit leo, viverra ac enim non, pulvinar aliquam nisl.
+Nam accumsan ac nisi at consectetur.
+Curabitur luctus lacus eget risus rutrum, vel facilisis urna feugiat.
+Ut ac dictum velit, in blandit augue.
+Fusce sit amet vehicula dui.
+Suspendisse eleifend tempor rhoncus.
+Cras vehicula, nisl et molestie pulvinar, lorem ex dictum augue, nec mollis leo sem quis mauris.
 
@@
 Nulla lacinia sapien sollicitudin, vestibulum nulla id, hendrerit nisl.
-
-Quisque pulvinar, enim a volutpat scelerisque, odio arcu condimentum velit, convallis vehicula velit augue id odio.
-Aenean ligula augue, mollis sit amet mi eu, ullamcorper aliquam massa.
-Aenean rutrum diam purus, eu porta mi blandit vitae.
-Phasellus luctus eleifend orci, nec aliquet mauris eleifend id.
-Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
-Sed elementum, magna sed finibus tincidunt, turpis orci viverra ligula, in sollicitudin nunc ex sed orci.
-Curabitur et purus tortor.
-Maecenas volutpat enim nisi, in ornare lectus venenatis id.
-In non enim dui.
-Suspendisse id eros in nisi consequat aliquet vel sed mi.
-Aenean placerat elementum semper.
 

### 2024-11-02 paper/paper.qmd
Updating the model, results, and appendix

@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Ut elit leo, viverra ac enim non, pulvinar aliquam nisl.
-Nam accumsan ac nisi at consectetur.
-Curabitur luctus lacus eget risus rutrum, vel facilisis urna feugiat.
-Ut ac dictum velit, in blandit augue.
-Fusce sit amet vehicula dui.
-Suspendisse eleifend tempor rhoncus.
-Cras vehicula, nisl et molestie pulvinar, lorem ex dictum augue, nec mollis leo sem quis mauris.
-In lacus massa, maximus vel vehicula in, tincidunt sed lorem.
-Proin commodo pulvinar dictum.
-Vestibulum eleifend, metus ac luctus molestie, velit odio cursus nisl, sed lobortis arcu massa id diam.
-Curabitur convallis erat a ultricies dictum.
-In imperdiet ultricies nibh, quis condimentum nulla mattis non.
+The table below summarizes the predicted support percentages for Donald Trump and Kamala Harris across the states where polling data is available.
+Due to the model being trained on a subset of the cleaned data and the specific approach used to split training and testing data, there are some missing values for each candidate.
+These missing values are expected and are discussed in further detail in the appendix.
+Additionally, in some cases, the sum of the predicted percentages for Trump and Harris slightly exceeds 100%, falling within a typical margin of error.
+This minor discrepancy is likely due to prediction error, which is also explored in the appendix.
 
-Aliquam erat volutpat.
-Praesent in erat sit amet purus auctor posuere ut vitae leo.
-Suspendisse potenti.
-Interdum et malesuada fames ac ante ipsum primis in faucibus.
-Ut blandit vel orci vel aliquam.
-Curabitur a turpis vestibulum enim interdum consectetur at et dui.
-Praesent ut mauris maximus, auctor nisl ac, eleifend sapien.
-Morbi non varius urna.
-Ut placerat vestibulum nisi in lacinia.
-Aliquam non ultrices arcu, et rhoncus dolor.
-Suspendisse vel pulvinar tortor.
-Nulla lacinia sapien sollicitudin, vestibulum nulla id, hendrerit nisl.
+Based on the predicted percentages, a winning candidate is identified for each state, assuming the winner takes all electoral votes for that state.
+As anticipated, both candidates are expected to secure wins in their respective stronghold states, with no predicted changes in non-swing states.
+This highlights the critical role of swing states, where a victory for either candidate could be decisive in the overall election outcome.
+The results underline the importance for both Trump and Harris to perform well in these battleground regions to secure their path to victory.
 
-```{r, echo = FALSE, message = FALSE, warning = FALSE}
+```{r, echo = FALSE, message = FALSE, warning = FALSE, fig.align='center'}
 #| label: tbl-prediction
@@
                                    "Trump", "Harris")) |>
-  kbl(booktabs = TRUE, col.names = c("State", "Predicted Harris %", "Predicted Trump %", "Electoral Votes", "Predicted Winner"))
+  kbl(booktabs = TRUE, col.names = c("State", "Harris %", "Trump %", "Electoral Votes", "Winner"))
 ```
@@
 
+The model evaluation relies on the F1 Score and RMSE (Root Mean Squared Error) as these metrics capture key aspects of prediction accuracy and reliability, aligning well with the paper’s objectives.
+The F1 Score, as the harmonic mean of precision and recall, is particularly useful here because it balances the model’s ability to correctly identify strong support for either candidate, ensuring both Trump and Harris’s predicted support is captured with minimal false positives and false negatives.
+This is essential in a political forecasting model, where the correct classification of state support is critical for predicting election outcomes.
+Meanwhile, RMSE provides insight into the overall prediction accuracy by measuring the average deviation of predictions from actual values.
+This helps gauge how well the model can approximate polling percentages, especially for swing states where slight errors can significantly impact projected outcomes.
+Together, these metrics ensure that the model is both precise in classification and accurate in magnitude, supporting the paper’s goal of making robust, actionable election predictions.
+
+# Additional Results Details
+
+## Null Values
+
+Some states in the summary table have null values in the predicted percentages for each candidate, which is due to the subsampling and splitting approach used in the model training process.
+Specifically, the model was trained on a subset of the cleaned dataset found in `data/analysis_data/analysis_data.parquet`, and when training and testing data were split, certain states did not have sufficient representation in both subsets.
+This led to gaps in the predictions for some states, as the model could not generalize well for locations with limited or no data during training.
+While these null values do not affect the core results, they highlight a limitation in the sampling approach, especially in states with fewer polling data points, and are further discussed with suggestions for improvement in the appendix.
+
+## Prediction Errors
+
+In some cases, the predicted percentages for Trump and Harris sum to slightly more than 100%, which reflects prediction error within an acceptable margin.
+This overestimation is consistent with the margin of error typically seen in polling averages, indicating that while the model is effective overall, minor discrepancies arise from rounding and the inherent variability in polling data.
+These errors can also result from the weights applied to pollsters based on their reliability scores, which may amplify certain pollster biases.
+To maintain accuracy, the model incorporates error margins similar to those in the polling data, ensuring predictions are within a reasonable range, with further analysis and adjustments explained in the appendix.
+
 # Polling Methodology Overview and Evaluation for Siena/NYT
@@
 
-# Appendix B: Idealized Methodology and Survey
+# Idealized Methodology and Survey
 
